\newcommand{\Pentry}{p_{\x[i]|\e[i]}}
\newcommand{\PPentry}{\sad{\Pentry}}
\newcommand{\sad}[1]{#1^{*}}
\newcommand{\rDist}{r}
\newcommand{\fExpand}{\intProd[\r]{\left( \fInside{\Pentry} \right)}}
\newcommand{\fInside}[1]{\sumixe \pi(\xeIt[i]) \ln \frac{\pi(\xIet[i])}{#1}}

\newcommand{\RR}{\sad{R}}
\newcommand{\Rdist}{R}
\newcommand{\Rvector}{\sad{R}_\Qset}
\newcommand{\RRvector}{\mathbf{\sad{R}_\Qset}}
\newcommand{\Cvector}{\mathbf{\central}}

\newcommandx{\f}[2][1 = \r, 2 = \Pvector, usedefault]{ f \ifthenelse{\isempty{#1}}{}{(#2, #1)}}
\newcommand{\fsad}{\f[\rr][\PPvector]}
\newcommandx{\fAlt}[2][1 = \r, 2 = \Pvector, usedefault]{\hat{f} \ifthenelse{\isempty{#1}}{}{(#2, #1)}}
\renewcommand{\r}{r}
\newcommand{\Pvector}{\mathbf{P_{\Qset}}}
\newcommand{\PvecSingle}{\mathbf{P}}
\newcommand{\rr}{\sad{\r}}
\newcommand{\PPvector}{\mathbf{\sad{P}_{\Qset}}}
\newcommand{\saddle}{(\PPvector, \rr)}
\newcommand{\rFixed}{\tilde{\r}}
\newcommand{\RFixed}{\tilde{R}}

\newcommand{\pDmax}{q}
\newcommand{\PDmax}{Q}
\newcommand{\PvecDmax}{\mathbf{Q_{\Qset}}}
\newcommand{\PvecDmaxEntry}{q_{\xIe[i]}}

The central distribution is essentially the solution to a minimax game.
By relaxing some constraints, this game can be converted into a convex-concave game.
It turns out that the solution to the relaxed problem always satisfies the constraints of the original problem, and is
feasible.
Since the solution to a convex-concave game corresponds to a saddle point,
by defining the appropriate function, we can characterize the central
distribution using standard convex optimization techniques.

\begin{definition} [Saddle Point]
    Consider a function $f:\set{w} \times \set{Z} \to \field{R}$.
    We refer to a pair $(w^*, z^*)$ as a saddle point for $f$, if we have
    \[
        f(w^*, z) \leq f(w^*, z^*) \leq f(w, z^*),
    \]
    for all $w \in \set{W}$ and $z \in \set{Z}$.
\end{definition}

\begin{lemma}
    \label{lm:saddle_conditions}
    Let \Mt be a parametric model, and \Xpairs be a query set.
    Let $\f[ ]$ be the function defined by:
    \begin{equation*}
        \f = \fExpand,
    \end{equation*}
    where $\r$ is a probability distribution, and $\Pvector$ is a vector of real numbers with an
    entry $\Pentry$ for every $i$, \x[i], and \e[i], such that $\sum_{\x[i]} \Pentry = 1$.
    Additionally, let $\Rdist$ denote the probability measure induced by $\r$.

    The point $\saddle$ is a saddle point for $\f[ ]$, if and only if there is a constant $\lambda$ and a function $\mu$,
    such that for any $i$, \x[i], \e[i], and \paramValue the following conditions hold:
    \begin{gather}
        \nonumber
        \fInside{\PPentry} - \mu(\paramValue) = \lambda, \\
        \label{eq:saddle_lm_pxIe}
        \PPentry = \RR(\xIe[i]), \\
        \nonumber
        \intProd[\rr]{} = 1, \\
        \label{eq:saddle_lm_r_geq_0}
        \rr(\paramValue) \geq 0, \\
        \nonumber
        \mu(\paramValue) \geq 0, \\
        \label{eq:saddle_lm_rmu_is_zero}
        \mu(\paramValue) \rr(\paramValue) = 0 \cdot
    \end{gather}

    Furthermore, a point $(\PvecDmax, \rFixed)$ minimizes $\f[\rFixed]$, with respect to $\Pvector$, if and only if it
    satisfies
    \begin{equation}
        \label{eq:saddle_lm_max_coverage}
        \PvecDmaxEntry = \RFixed(\xIe[i]),
    \end{equation}
    for all $i$, \x[i], and \e[i].
\end{lemma}

\begin{proof}
    We define
    \begin{equation*}
        \fAlt = \fExpand,
    \end{equation*}
    where $\r$ is a real function of the model parameter \paramValue, and $\Pvector$ is a vector of real
    numbers with an entry $\Pentry$ for every $i, \xe[i]$.

    Let $\saddle$ be a simultaneous solution to the following two optimization problems:

    \begin{equation}
        \begin{aligned}
            &\text{minimize} & &\fAlt[\r] & &\text{w.r.t.} \ \Pvector \\
            &\text{subject to} & &\sum_{\x[i]} \Pentry = 1,  & &\text{for all}\  i,\e[i] \\
            \\
            &\text{maximize} & &\fAlt[][\Pvector] & &\text{w.r.t.} \ \r \\
            &\text{subject to} & &\r(\paramValue) \geq 0, & &\text{for all} \ \paramValue  \\
            & & &\intProd[\r]{} = 1 &
        \end{aligned}\label{eq:twin_optimization}
    \end{equation}
    Clearly, if $\saddle$ exists, it will be a saddle point for $\f[ ]$.

    Both of these optimization problems are convex~\cite{0521833787} and differentiable.
    To establish this, consider that all the constraint functions are affine, and therefore are convex and
    differentiable.
    Note that for the constraint $\r(\paramValue) \geq 0$, for each \paramValue, we can define an affine
    constraint function of the form \[ \int \delta(\paramValue - t) \r(t) dt \geq 0,\] where $\delta$ is
    the Dirac delta function.

    Additionally, $\fAlt[ ]$ is differentiable function with respect to both $\r$ and $\Pvector$.
    For any fixed $\Pvector$, $\fAlt[\cdot]$ is an affine function and is concave.
    For a fixed solution to the second optimization problem denoted by $\rFixed$, we can write
    \begin{equation}
        \label{eq:simplified_f}
        \fAlt[\rFixed][\Pvector] = c - \sumixe \RFixed(\xe[i]) \ln \Pentry,
    \end{equation}
    where $c$ and $\RFixed(\xe[i]) = \marginal[\rFixed]{\xe[i]}$ are not functions of $\Pvector$.
    Since $\rFixed$ is a solution to the second optimization problem, it satisfies the constraints
    of the second problem and is a distribution.
    Therefore, for all $i, \xe[i]$ we have $\RFixed(\xe[i]) \geq 0$, and $\fAlt[\rFixed][\cdot]$ is
    the negative of a linear combination of concave $\ln \Pentry$ functions with nonnegative coefficients.
    This function is convex.

    Thus, both optimization problems are convex and differentiable, with affine constraints.
    The constraints simply restrict the feasible set to the set of probability distributions, and it is always possible
    to find feasible points that meet all the constraints.
    Therefore, Slater’s condition is satisfied, and the KKT conditions provide necessary
    and sufficient conditions for optimality~\cite{0521833787}.
    In other words, If a point $\saddle$ satisfies the KKT conditions for both problems, it will be a saddle
    point for $\f[ ]$, and vice versa.
    The following KKT conditions are obtained for every \paramValue, $i$, \x[i], and \e[i]:
    \begin{gather}
        \label{eq:kkt_proof_R_is_pxIe}
        \intProd[\rr]{\pi(\xeIt[i])} = \lambda(\e[i]) \PPentry, \\
        \label{eq:kkt_proof_pxIe_sums_one}
        \sum_{\x[i]} \PPentry = 1, \\
        \nonumber
        \fInside{\PPentry} - \mu(\paramValue) = \lambda, \\
        \label{eq:kkt_proof_r_sums_one}
        \intProd[\rr]{} = 1, \\
        \nonumber
        \rr(\paramValue) \geq 0, \\
        \nonumber
        \mu(\paramValue) \geq 0, \\
        \nonumber
        \mu(\paramValue) \rr(\paramValue) = 0 \cdot
    \end{gather}

    By summing Equation~\ref{eq:kkt_proof_R_is_pxIe} over \x[i] and using Equation~\ref{eq:kkt_proof_r_sums_one},
    we obtain
    \[
        \lambda(\e[i]) = \marginal[\rr]{\e[i]} \cdot
    \]
    Then, we can combine Equation~\ref{eq:kkt_proof_R_is_pxIe} and~\ref{eq:kkt_proof_pxIe_sums_one} as follows:
    \[
        \PPentry = \frac{\marginal[\rr]{\xe[i]}}{\marginal[\rr]{\e[i]}} = \RR(\xIe[i]) \cdot
    \]

    Equations~\ref{eq:kkt_proof_R_is_pxIe} and~\ref{eq:kkt_proof_r_sums_one} are the KKT conditions for the
    minimization problem in~\ref{eq:twin_optimization}.
    Therefore, by assuming $\rDist$ is a probability distribution, these conditions provide
    necessary and sufficient conditions for a point to be a minimizer of $\f[\rFixed][\cdot]$ for a fixed $\rFixed$.
    Equation~\ref{eq:saddle_lm_max_coverage} combines these two equations and the assumption that
    $\rDist$ is a distribution into a single expression.
%
%    \newcommand{\KLforEi}{\D[{\XIe[i]}][\RFixed][\PvecSingle]}
%
%    Using simple algebra, we observe that for any arbitrary fixed distribution $\rFixed$, we have
%    \[
%        \min_{\Pvector} \f[\rFixed] = \max_{\Pvector} \sumixe \RFixed(\xe[i]) \ln \Pentry,
%    \]
%    where $\RFixed(\xe[i]) = \marginal[\rFixed]{\xe[i]}$.
%
%    Since $\Pentry \geq 0$ and $\sum_{\x[i]} \Pentry = 1$, we can define the Kullback–Leibler
%    divergence between $\Pentry$ entries with the same \e[i] and $\RFixed(\XIe[i])$.
%    We denote this value by $\KLforEi$.
%    The KL divergence is always nonnegative, and therefore
%    \[
%        \sum_i \Ex{\RFixed}{\KLforEi} \geq 0,
%    \]
%    which can be simplified to
%    \[
%        \sumixe \RFixed(\xe[i]) \ln \Pentry \leq \sumixe \RFixed(\xe[i]) \ln \RFixed(\xIe[i])\cdot
%    \]
%    We can reach the upper bound at the right hand side by letting $\Pentry \coloneqq \RFixed(\xe[i])$.
\end{proof}

Next, we will establish the connection between the saddle point and the central distribution.
We also show that there is a strong relationship between central distributions and
Bernardo's reference priors~\cite{BERNARDO200517}.

One significant insight provided by the next theorem is that it suggests inference and searching for a central
distribution can be combined and performed simultaneously by finding a saddle point for $\f[ ]$.

\begin{definition} [Coverage]
    Let \pmodel be a parametric model, and \Qset be a query set.
    Let $p$ be a prior distribution, and $\inP{P}$ be the probability measure induced by $p$.
    We define the \emph{coverage of $p$ for \Qset} as
    \begin{equation*}
        \Cx = \CxExpand \cdot
    \end{equation*}
\end{definition}

The coverage $\Cx$ is the dual of the divergence $\Dx$.
For a query set, as we decrease the divergence, the coverage increases.

\begin{theorem}
    \label{th:saddle_is_central}
    Let \pmodel be a generic parametric model and \Xpairs be a query set.
    Consider the function $\f[ ]$ introduced in Lemma~\ref{lm:saddle_conditions}.
    If $\f[ ]$ has a saddle point, denoted by $\saddle$, then $\RR$, the probability measure induced by
    $\rr$, is a central distribution for \Qset.
    Moreover, $\rr$ has the maximum coverage in \Mt.
\end{theorem}

\begin{proof}
    \newcommand{\PP}{P^{*}}
    Suppose \central is a central distribution for \Qset, and $\saddle$ is a saddle point for $\f[ ]$.
    Clearly, the point $(\Cvector, \rr)$, where  $\Cvector$ is the vector of $\central(\xIe[i])$
    probabilities, is in the domain of $\f[ ]$.
    Since $\saddle$ is a saddle point for $\f[ ]$, we have
    \begin{equation}
        \label{eq:th_proof_saddle_lq_dx}
        \f[\rr][\PPvector] \leq \f[\rr][\Cvector] \cdot
    \end{equation}
    Notice that the definition of $\f[ ]$ implies:
    \[
        \f[\rr][\Cvector] = \intProd[\rr]{\DxCond[\central]} \cdot
    \]
    Because $\rr$ is a probability distribution and integrates to one we have
    \[
        \intProd[\rr]{\DxCond[\central]} \leq \supParam \DxCond[\central] = \Dx[\central],
    \]
    and
    \[
        \f[\rr][\PPvector] \leq \Dx[\central] \cdot
    \]

    \Mt is a generic parametric model, and therefore $\inP{\RR}$, where $\RR$ is the probability measure induced by $\rr$.
    Given that $\saddle$ is a saddle point for $\f[ ]$, by Lemma~\ref{lm:saddle_conditions}, the entries of $\PPvector$
    satisfy Equation~\ref{eq:saddle_lm_pxIe}.
    Consequently, for the divergence measure of $\RR$, we can write
    \begin{align*}
        \Dx[\RR] &= \supParam \DxCond[\RR] \\
        &= \max_{\r} \intProd[\r]{\DxCond[\RR]}\\
        &= \max_{\r} \f[\r][\PPvector] \\
        &= \fsad,
    \end{align*}
    where $\r$ denotes a probability distribution.
    Thus, Inequality~\ref{eq:th_proof_saddle_lq_dx} implies
    \[
        \Dx[\RR] \leq \Dx[\central] \cdot
    \]
    Since $\inP{\RR}$, we must have $\Dx[\RR] = \Dx[\central]$, and $\RR$ is a central distribution for \Qset.


    Let $\pDmax$ be an arbitrary prior distribution, and $\PDmax$ be the induced probability measure
    by $\pDmax$.
    Let $\PvecDmax$ represent the vector of $\PDmax(\xIe[i])$ probabilities.
    By the definition of $\f[ ]$, we have
    \[
        \Cx[\pDmax] = \f[\pDmax][\PvecDmax] \cdot
    \]
    The point $(\PvecDmax, \pDmax)$ satisfies Equation~\ref{eq:saddle_lm_max_coverage}, and
    by Lemma~\ref{lm:saddle_conditions}, minimizes $\f[\pDmax][\cdot]$.
    Therefore,
    \[
        \f[\pDmax][\PvecDmax] \leq \f[\pDmax][\PPvector] \cdot
    \]
    On the other hand, $\saddle$ is a saddle point for $\f[ ]$, and
    \[
        \f[\pDmax][\PPvector] \leq \fsad \cdot
    \]
    By Lemma~\ref{lm:saddle_conditions}, any saddle point for $\f[ ]$, satisfies Equation~\ref{eq:saddle_lm_pxIe}.
    That implies
    \[
        \Cx[\rr] = \fsad \cdot
    \]
    Thus, we have
    \[
        \Cx[\pDmax] \leq \Cx[\rr],
    \]
    and $\rr$ has the maximum coverage.
\end{proof}

Back to our dice example, we continue from Equation~\ref{eq:joint_form}, and calculate the coverage of a prior
distribution $p$ for the query set $\Qset = \{\X\}$, where \X is the sample space of $n$ dice rolls:
\begin{align*}
    \Cx &= \CxExpand \\
    &= \int \KlCond[][\seqRval{n}][ ] \dt \\
    &= \int \sum_{\seqRval{n}} p(\seqRval{n}, \paramValue) \ln
    \frac{p(\paramValue \mid \seqRval{n})}{p(\paramValue)} d\paramValue \cdot
\end{align*}

We see that the central distribution for our dice example, when we consider a query set equivalent to the
sample space, is the probability measure that is obtained by using the reference prior~\cite{BERNARDO200517} for
the multinomial parameters.

With the next theorem, we finally see why we refer to these distributions as ``central.''
Exactly like the center of a circle, the central distribution is equidistant from the boundary.

\begin{theorem} [Centrality]
    \label{th:lambda}
    Let \pmodel be a generic parametric model, and \Xpairs be a query set.
    Suppose $\inP{\central}$ is a probability measure induced by a strictly positive prior distribution.
    If there is a constant $\lambda$ such that
    \begin{equation*}
        \DxCond[\central] = \lambda,
    \end{equation*}
    then \central is a central distribution for \Qset.
\end{theorem}

\begin{proof}
    Lemma~\ref{lm:saddle_conditions} provides a set of sufficient conditions for a saddle point of $\f[ ]$.
    Note that more restrictive conditions can also be imposed to derive an alternative set of sufficient conditions
    for a saddle point.
    Consequently, we can replace Inequality~\ref{eq:saddle_lm_r_geq_0} with the more
    restrictive $\rr(\paramValue) > 0$ condition.
    By Equation~\ref{eq:saddle_lm_rmu_is_zero}, that implies $\mu(\paramValue) = 0$,
    and Lemma~\ref{lm:saddle_conditions} conditions can be simplified to
    \begin{gather*}
        \fInside{\PPentry} = \lambda, \\
        \PPentry = \RR(\xIe[i]), \\
        \intProd[\rr]{} = 1,\quad \rr(\paramValue) > 0 \cdot
    \end{gather*}

    Let $\inP{\central}$ be a probability measure, induced by a strictly positive prior $\cMass{}$.
    If for some constant $\lambda$, we have $\DxCond[\central] = \lambda$, we see that the point $(\Cvector, \cMass{})$
    satisfies these simplified conditions, where $\Cvector$ is the corresponding vector of $\central(\xIe[i])$
    probabilities.

    Therefore, Lemma~\ref{lm:saddle_conditions} implies that $(\Cvector, \cMass{})$ is a saddle point for $\f[ ]$.
    Since \Mt is a generic parametric model, Theorem~\ref{th:saddle_is_central} implies \central is a central
    distribution for \Qset.
\end{proof}
