In this section, we explore the process of deriving central distributions for parametric models.
Our definition of parametric models is quite broad, entailing any model whose set of probability measures can be
indexed by a finite-dimensional real vector.
However, to establish a structured framework for identifying central distributions, we must refine this definition
to include only models where the set of probability measures is isomorphic to a convex set.

\begin{definition}[Generic Parametric Model]
    We say a parametric model \pmodel is \emph{generic}, if for any arbitrary probability distribution $r$,
    there is a probability measure $R \in \set{P}$, such that for every $\rval[]{s} \in \set{s}$
    \[
        \marginalEq[r]{\rval[]{s}}\cdot
    \]
\end{definition}

In a parametric model, the maximum of divergence happens for a prior distribution
that is concentrated at a single value of the parameter $\paramValue$.
That means, for a parametric model, which allows any high peak prior, instead of maximizing over the set of
all acceptable distributions, we can simply maximize over the parameter space, using the conditional version
of the divergence measure.

\begin{lemma}
    \label{lm:DxP_uppper_bound}
    Assume that \pmodel is a parametric model.
    Let \Xpairs be a query set in \Mt.
    For every $P \in \set{P}$ we have
    \begin{equation*}
        \Dx \leq \supParam \DxCond \cdot
    \end{equation*}
\end{lemma}

\begin{proof}
    \newcommand{\RP}{\sumixe \pi(\xeIt[i]) \ln \frac{R(\xIe[i])}{P(\xIe[i])}}

    Let $R$ and $P$ be two arbitrary probability measures in \Mt.
    For any parameter value \paramValue we have:
    \[
        \DxCond[P] - \DxCond[R] = \RP \cdot
    \]
    The conditional divergence is nonnegative and we have
    \[
        \RP \leq \DxCond \cdot
    \]
    This inequality holds for every \paramValue.
    Therefore, the supremum of the right-hand side w.r.t. \paramValue is also greater than or equal to the
    supremum of the left-hand side:
    \begin{equation}
        \supParam \RP \leq \supParam \DxCond \cdot
        \label{eq:ineq-theorem1}
    \end{equation}
    Trivially, for any \paramValue we have
    \[
        \RP \leq \supParam \RP \cdot
    \]
    \Mt is a parametric model and $\marginalEq[R]{\xe[i]}$, where $r(\paramValue)$ is
    a prior probability distribution.
    Since the above inequality holds for every value of \paramValue and $r(\paramValue) \geq 0$, we can multiply both
    sides by $r(\paramValue)$, and integrate.
    Notice that the right hand side is not a function of $\paramValue$ and it remains unchanged
    because $\int \dt[r] = 1$:
    \[
        \DxExpand[R] \leq \supParam \RP\cdot
    \]
    Now from Inequality~\ref{eq:ineq-theorem1}, for \emph{any} $P \in \set{P}$ and $R \in \set{P}$, it
    follows that
    \[
        \DxExpand[R] \leq \supParam \DxCond,
    \]
    which proves the lemma.
\end{proof}

\begin{theorem}
    \label{th:Dx_parametric_form}
    Suppose \pmodel is a parametric model, and let $\Xpairs$ be a query set in \Mt.
    If for every $\epsilon > 0$ and every value of the parameter $\paramValue$, there exists a distribution $R \in \set{P}$
    such that
    \begin{equation}
        \DxCond[][\paramValue] - \DxExpand[R]  < \epsilon,
        \label{eq:epsilon_close}
    \end{equation}
    then for any $P \in \set{P}$ we have:
    \begin{equation}
        \Dx = \supParam \DxCond  \cdot
        \label{eq:div_parametric}
    \end{equation}
    \label{th:div_for_parametric}
\end{theorem}

\begin{proof}
    Assume, for the sake of contradiction, that
    \[
        \Dx \neq \supParam \DxCond \cdot
    \]
    Then, Lemma~\ref{lm:DxP_uppper_bound} implies $\Dx < \supParam \DxCond$.
    Supremum is the minimal upper bound of a set.
    That means $\Dx$ can not be an upper bound for the set of values of $\DxCond$,
    and there should exist a $\paramValue^{*}$ such that
    \[
        \DxCond[][\paramValue^{*}] > \Dx \cdot
    \]

    By the theorem assumption, for $\paramValue^{*}$ and $\epsilon = \DxCond[][\paramValue^{*}] - \Dx$ there should be a
    distribution $R \in \set{P}$ such that Equation~\ref{eq:epsilon_close} holds, and
    \begin{align*}
        \DxExpand[R] > \Dx  \cdot
    \end{align*}
    On the other hand
    \[
        \supQ \DxExpand[Q] \geq \DxExpand[R] \cdot
    \]
    Notice that the left hand side is $\Dx$.
    This contradiction implies that the assumption can not hold.
    Hence,
    \[
        \Dx = \supParam \DxCond. \qedhere
    \]
\end{proof}

\begin{proposition}
    A generic parametric model satisfies the conditions of Theorem~\ref{th:Dx_parametric_form}.
\end{proposition}

\input{minimax}

\input{fpoint}
