Intuitively, a central distribution acts as a representative or summary of a set of distributions.
While it may not belong to the set itself, it reflects the overall behavior of the set in a way that is meaningful
for inference and for evaluating other distributions.
It provides a meaningful way to compare distributions based on our partial knowledge.

\begin{definition}[Central Divergence]
    \label{def:central-divergence}
    For any distribution $P$, we define the \emph{central divergence} of $P$ from a set of distributions \setQ, with
    respect to a random variable $X$, as follows:
    \begin{equation*}
        \myDiv = \inf_{\cDist} \kl[{\cDist}],
    \end{equation*}
    where $\cDist$ denotes a central distribution of \setQ for $X$.
\end{definition}

Note that when \setQ has a unique central distribution, the central divergence is simply defined as the KL divergence
from that unique central distribution.

\begin{definition}
    \label{def:set-of-sets}
    Let $X$ be a random variable, and let \setQQ be a set whose elements are sets of distributions over $X$.
    Let \cDist[\setQ] be a central distribution of $\setQ \in \setQQ$ for $X$.
    We say \ccDist is a central distribution of \setQQ, if for every probability distribution $P$ we have:
    \begin{equation*}
        \sup_{\setQ \in \setQQ} \myDiv[\ccDist(X)]  \leq \sup_{\setQ \in \setQQ} \myDiv,
    \end{equation*}
    where $\myDiv[\, \cdot \,]$ refers to the central divergence as defined in Definition~\ref{def:central-divergence}.
\end{definition}

Suppose we wish to model an exchangeable sequence of random variables.
Let $S_n$ denote the sequence of the first $n$ variables: $S_n = (\seqExp{X})$.
As discussed earlier, exchangeability can be interpreted as a form of partial knowledge, which allows us to
represent our uncertainty using a central distribution over $S_n$.

However, this central distribution generally depends on the sequence length $n$.
According to the principle of objectivity, our beliefs should not depend on the specifics of our experimental setup,
and in particular, should not vary with the length of the sequence.

It is important to note that a distribution defined over a longer sequence induces marginal distributions over its
shorter subsequences.
This observation suggests that, in order to satisfy the principle of objectivity, we may instead determine a central
distribution over an infinite exchangeable sequence, from which the distributions of all finite initial segments can
be derived.

This requires constructing a central distribution that is well-defined over $S_{\infty}$.

\begin{definition}
    Let \infSeq{S} be a sequence of random variables and \setQ be a set of probability measures,
    where each element of \setQ defines a distribution over each $S_n$.
    Assume \cDist[n] is a central distribution for $S_n$.
    Let \cDist be a probability measure that defines a distribution over every $S_n$.
    \cDist is a central distribution of \setQ for \infSeq{S}, if we have
    \begin{equation*}
        \lim_{n \to \infty} \kl[{\cDist[n]}][\cDist][S_n] = 0 \cdot
    \end{equation*}
\end{definition}

Intuitively, this definition states that as $n \to \infty$ the distribution that $C$ induces over $S_n$ becomes
increasingly similar to a central distribution for $S_n$.
In other words, \cDist is a central distribution for $S_{\infty}$.

If we have a consistent estimator sequence for the index of a set, the following theorem provides a way to construct a
central distribution for that estimator.

Here, by a consistent estimator we mean a sequence of estimators such that, for any fixed index value, the
distribution of each estimator $\est_n$ becomes increasingly concentrated around the corresponding value of the
index as $n$ increases.

\begin{theorem}
    \label{th:central-by-estimator}
    Let \infSeq{\est} be a sequence of random variables, and let \setQ be a set of probability measures,
    where each element of \setQ defines a distribution over each $\est_n$.
    Assume that \setQ can be indexed by a finite-dimensional vector \param.
    If \infSeq{\est} is a consistent sequence of estimators for \param, and there exists a sequence of
    constants \infSeq{\lambda} such that the sequence
    $\infSeq[]{\lambda_n -\entropy{Q}{\est_n \mid \paramVal}}$ converges
    for every value of \paramVal, then
    \begin{equation*}
        \cPrior(\paramVal) \propto \lim_{n \to \infty} \exp
        \left\{ \lambda_n -\entropy{Q}{\est_n \mid \paramVal} \right\},
    \end{equation*}
    is a central prior of \setQ for \infSeq{\est}.
\end{theorem}

When dealing with layered ignorance and attempting to determine the central distribution of a set of sets of
distributions, as defined in Definition~\ref{def:set-of-sets}, we typically consider the case where the number of
such sets is finite.

In this setting, and under appropriate conditions, the central distribution reduces to the uniform distribution.

\begin{corollary}
    \label{cor:center-of-countable}
    Under the assumptions of Theorem~\ref{th:central-by-estimator}, if \setQ is a countable set indexed by a discrete
    random variable $I$, then $c(i) \propto 1$ is a central prior of \setQ for \infSeq{\est}.
\end{corollary}

A central distribution over an estimator cannot, by itself, be used to perform inference at the level of observed
outcomes.
To do so, we must convert it into a distribution over the primary variables of interest.
Theorem~\ref{th:estimator-to-var} provides a simple way for carrying out this conversion.

As an illustrative example, consider a binomial experiment.
Theorem~\ref{th:central-by-estimator} allows us to determine a central distribution over the number of successes.
However, for inference, we typically require a distribution over specific ordered sequences of successes and failures.
Theorem~\ref{th:estimator-to-var} enables this by offering a natural approach: we assign a uniform
distribution over all sequences with the same number of successes and failures.
