%! Author = aybehrouz
%! Date = 7/10/25


\newcommand{\util}[1][a]{\ell(#1, x)}
\newcommand{\envDist}{P^*}
\newcommand{\post}{\pi(x_i \mid \paramVal)}


We begin by revisiting a fundamental decision-making problem, and how it is treated within the framework of Bayesian
decision theory.

Consider an environment where an agent must select an action from a set of available actions.
The loss associated with each action depends on the unknown state of the environment
and can be quantified by a real number.
Specifically, let $a$ denote an action, and $x$ represent the unknown environment state.
The loss function  $\util$ quantifies the loss for each action.

Furthermore, we assume that an evidence $e$ of this unknown environment state exists, and the agent can leverage
this evidence to determine the best action.
In other words, our agent aims to find an optimal strategy, where a strategy defines the distribution of each
action conditioned on the observed evidence: $S(A \mid E)$.

According to Bayesian decision theory, the optimal strategy is the one that minimizes the expected loss:
\begin{equation*}
    S_{\text{opt}} = \arg\min_S\sum_a\sum_{x,e} \util S(a \mid e)\envDist(x, e),
\end{equation*}
where $\envDist$ is the joint probability distribution of the environment state and the evidence.

It can be shown that there always exists a deterministic optimal strategy.
That is, we can consider a strategy as a function of the evidence, rather than as a conditional distribution:
\[
    S_{\text{opt}} = \arg\min_S \sum_{x,e} \util[S(e)] \envDist(x, e).
\]
A strategy that, for each evidence $e$, selects the action minimizing the expected loss conditioned
on $e$, is optimal:
\begin{align*}
    S_{\text{opt}}(e) &= \arg\min_a \Ex{\envDist}{\util \mid e} \\
    &= \arg\min_a\sum_x \util \envDist(x \mid e) \cdot
    \label{eq:bayes-action}
\end{align*}

Now, suppose that we decide to use a different evidence $E'$ instead of $E$.
Could this change potentially improve our strategy?
Within the framework of Bayesian decision theory, we can easily answer this question:
To compare any two strategies, we can simply compare their expected loss.
The strategy with the lower expected loss is the better one.

Note that, in reality, we cannot freely choose any random variable as our evidence.
We can only choose evidence that is a deterministic function of the evidence provided by the environment,
allowing us to determine its value after observing the original evidence.
Utilizing a strategy that uses a simpler evidence, resembles feature selection in machine learning.
For instance, in a learning task where our evidence is an image, we might substitute the image with the first
three coefficients of its Fourier transform.
Naturally, these coefficients are a function of the original evidence.

Interestingly, if we assume $E' = f(E)$, it turns out
that, according to our Bayesian framework, the optimal strategy for $E$ is always
better than any strategy that uses $E'$.
Thus, at first glance, it appears that Bayesian decision theory does not favor feature selection.

From a certain perspective, it could be argued that adopting a strategy which uses simpler evidence may lead to
ignoring some parts of useful available information, and therefore is not justified by Bayesian
decision theory.
However, in practice we rather to use feature selection because without it the original learning task requires
impractical large datasets.

The key point here is that the space of strategies using $E'$ is a subset of the strategies that use $E$.
When we are searching for the best strategy based on $E$, we are implicitly evaluating all simpler forms as well.

We believe that this is why the Bayesian framework does not favor the simpler evidence $E'$.
Plausibly, if we choose an appropriate prior distribution, when we are finding the optimal
strategy, feature selection should be performed automatically within the Bayesian framework.
However, many commonly used non-informative priors, such as the flat prior, do not exhibit feature
selection characteristics.

Throughout this discussion, we will explore a systematic approach for finding a noninformative prior that also
exhibit feature selection characteristics.


