\section{Latent Regression Model}

\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\normsq}[1]{\left\lVert #1 \right\rVert^2}
\newcommand{\trans}[1]{#1^\top}
\newcommand{\Gam}[3]{\mathrm{Gamma} \left( #1 \;\middle|\; #2, #3\right)}
\newcommand{\Nor}[3]{\mathcal{N} \left( #1 \;\middle|\; #2, #3 \right)}
\newcommand{\avgz}{\overline{z}}
\newcommand{\avgzz}{\overline{zz}}
%\newcommand{\Ex}[2]{E_{#1} \left\[{#2} \right\]}

We consider $C$ classes (or datasets), indexed by $c = 1, \dots, C$.
For each class $c$, we observe a data matrix
$X^{(c)} \in \mathbb{R}^{N_c \times M}$, where each row
$\vect{x}_i^{(c)} \in \mathbb{R}^M$ is associated with a
$D$-dimensional latent variable $\vect{z}_i^{(c)} \in \mathbb{R}^D$.

Thus, each class is associated with a collection of latent variables
\[
    \vect{z}^{(c)} = \{\vect{z}_i^{(c)}\}_{i=1}^{N_c},
    \qquad \vect{z}_i^{(c)} \in \mathbb{R}^D.
\]

For each class $c$, the latent variables are assumed independent and identically distributed according to
\[
    \vect{z}_i^{(c)}
    \sim
    \mathcal{N}\!\left(\vect{\mu}^{(c)}, \tau_c^{-1} I_D \right),
    \qquad
    c = 2, \dots, C,
\]
where $\vect{\mu}^{(c)} \in \mathbb{R}^D$ is the class-specific latent mean and
$\tau_c > 0$ is a precision parameter controlling the latent dispersion.

To remove redundancy, we fix the latent distribution of the first class
as a reference coordinate system.
Specifically, we impose
\[
    \vect{\mu}^{(1)} = \vect{0},
    \qquad
    \tau_1 = 1,
\]
so that
\[
    \vect{z}_i^{(1)} \sim \mathcal{N}(\vect{0}, I_D).
\]

This anchoring removes global translation and scaling symmetries
without restricting the expressive capacity of the model.
The latent geometry of each class is therefore interpreted
relative to the reference class $c=1$.

Let $\phi: \mathbb{R}^D \to \mathbb{R}^K$ denote a fixed nonlinear basis mapping.
The design matrix of class $c$ is defined as
$Z^{(c)} \in \mathbb{R}^{N_c \times K}$ with entries
\[
    Z^{(c)}_{ik} = \phi_k(\vect{z}_i^{(c)}).
\]

We collect the decoder weights in a shared matrix
\[
    W = [\vect{w}_1 \ \dots \ \vect{w}_M]
    \in \mathbb{R}^{K \times M},
\]
where each column $\vect{w}_j \in \mathbb{R}^K$ corresponds to the weights for the $j$-th observed dimension
across all classes.

Conditioned on $\vect{z}^{(c)}$ and $W$, observations are generated as
\[
    p(X^{(c)} \mid \vect{z}^{(c)}, W)
    =
    \prod_{i=1}^{N_c}\prod_{j=1}^M
    \Nor{x_{ij}^{(c)}}{\phi(\vect{z}_i^{(c)})^\top \vect{w}_j}{\beta_j^{-1}},
\]
or equivalently,
\[
    \vect{x}_j^{(c)}
    \sim
    \mathcal{N}\!\left(Z^{(c)} \vect{w}_j, \beta_j^{-1} I_{N_c} \right),
\]
where $\vect{x}_j^{(c)}$ denotes the $j$-th column of $X^{(c)}$
and $\beta_j > 0$ is the observation precision of that column.

To regularize the decoder,
we assume noninformative priors for the latent parameters
$\{\vect{\mu}^{(c)}, \tau_c\}_{c=2}^C$,
and place independent Gaussian priors on the columns of $W$:
\[
    p(W)
    =
    \prod_{j=1}^{M}
    \Nor{\vect{w}_j}{\vect{0}}{\alpha_j^{-1} I_K}.
\]

The full joint distribution factorizes as
\[
    p(W)
    \prod_{c=1}^C
    p(X^{(c)} \mid \vect{z}^{(c)}, W)
    p(\vect{z}^{(c)} \mid \vect{\mu}^{(c)}, \tau_c)
    p(\vect{\mu}^{(c)}, \tau_c).
\]

This defines a shared nonlinear generative model in which
all classes are coupled through the common decoder $W$,
while retaining class-specific latent geometry via
$(\vect{\mu}^{(c)}, \tau_c)$.

\subsection{Variational Inference for the Single-Class Case}

To simplify the exposition, we now consider the single-class case.
Since only one class is present, we remove the superscript $(c)$
from the notation for clarity.

Furthermore, we restrict the latent variable to be scalar,
\[
    \vect{z} = \{z_i\}_{i=1}^N
    \qquad
    z_i \in \mathbb{R},
\]
so that
\[
    p(\vect{z} \mid \mu, \tau)
    =
    \prod_{i=1}^N
    \mathcal{N}(z_i \mid \mu, \tau^{-1}).
\]
We treat $\mu$ and $\tau$ as unknown parameters to be inferred,
using the standard joint Jeffreys prior for the mean and precision of a Gaussian model,
\[p(\mu, \tau) \propto \tau^{-1}.\]

The nonlinear basis mapping reduces to
\[
    \phi : \mathbb{R} \to \mathbb{R}^K,
\]
and the design matrix $Z \in \mathbb{R}^{N \times K}$ is defined by
\[
    Z_{ik} = \phi_k(z_i).
\]

We see the Bayesian network of this model in Figure~\ref{fig:regression_bayes_net}.
Exact posterior inference in this model is intractable
due to the nonlinear dependence of the likelihood on $\vect{z}$.
We therefore proceed by introducing a variational approximation.

\begin{figure}[t]
    \centering
    \begin{tikzpicture}

% Nodes
        \node[latent] (mu) {$\mu$};
        \node[latent, right=of mu] (tau) {$\tau$};
        \node[latent, below=of mu] (z) {$z_i$};
        \node[obs, below=of z] (X) {$X_{ij}$};
        \node[latent, right=of X] (W) {$\vect{w}_j$};

% Edges
        \edge {mu,tau} {z};
        \edge {z,W} {X};

% Plates
        \plate {plate1} {(z)(X)} {$N$};
        \plate {plate2} {(X)(W)} {$M$};

    \end{tikzpicture}
    \caption{One class scalar latent regression model}\label{fig:regression_bayes_net}
\end{figure}

In order to formulate a variational treatment of this model,
we consider a variational distribution which factorizes between the latent
variables and the parameters so that
\[
    q(\vect{z}, W, \mu, \tau) = q(\vect{z})q(W, \mu, \tau).
\]

First, let us consider the derivation of the update equation for the factor $q(W, \mu, \tau)$.
The log of the optimized factor is given by
\begin{equation*}
    \ln q^*(W, \mu, \tau)
    = \Ex{q(\vect{z})}{\ln p(W, \mu, \tau \mid \vect{z}, X)} + \text{const}.
\end{equation*}
As can be seen from Figure~\ref{fig:regression_bayes_net}, the d-separation criterion implies that
\begin{equation*}
    \Ex{q(\vect{z})}{\ln p(W, \mu, \tau \mid \vect{z}, X)} =
    \Ex{q(\vect{z})}{\ln p(\mu, \tau \mid \vect{z})} +
    \sum_j \Ex{q(\vect{z})}{\ln p(\vect{w}_j \mid \vect{z}, X)}.
\end{equation*}
Therefore, we have the following induced factorization for $q(W, \mu, \tau)$:
\begin{equation*}
    q(W, \mu, \tau) =  q(\mu, \tau) \prod_{j=1}^M q(\vect{w}_j).
\end{equation*}

We obtain $q(\vect{w}_j)$ using the fact that each $\vect{w}_j$ is a weight vector of a Bayesian linear regression
model:
\begin{align*}
    \ln p(\vect{w}_j \mid \vect{z}, X) &= -\hf[\beta_j] \normsq{Z\vect{w}_j - \vect{x}_j} -
    \hf[\alpha_j] \trans{\vect{w}_j} \vect{w}_j + \text{const} \\
    &= -\hf \trans{\vect{w}_j} (\beta_j \trans{Z}Z + \alpha_j I) \vect{w}_j +
    \beta_j \trans{\vect{x}_j} Z \vect{w}_j + \text{const}.
\end{align*}
Taking the expectation with respect to $q(\vect{z})$, we obtain
\begin{equation*}
    \ln q^*(\vect{w}_j) = -\hf \trans{\vect{w}_j} (\beta_j \Ex{}{\trans{Z}Z} + \alpha_j I)
    \vect{w}_j +
    \beta_j \trans{\vect{w}_j} \trans{\Ex{}{Z}} \vect{x}_j + \text{const},
\end{equation*}
where expectations of matrices are taken element-wise.
The resulting expression is quadratic in $\vect{w}_j$.
Completing the square yields
\begin{equation*}
    q^*(\vect{w}_j) = \mathcal{N}(\vect{w}_j \mid \vect{\mu}_j, \Sigma_j).
\end{equation*}
The corresponding moments are
\begin{align*}
    \Ex{}{\vect{w}_j} &= \vect{\mu}_j, \\
    \Ex{}{\vect{w}_j \trans{\vect{w}_j}} &= \vect{\mu}_j \trans{\vect{\mu}_j} + \Sigma_j,
\end{align*}
with
\begin{align*}
    \Sigma_j^{-1} &= \beta_j \Ex{}{\trans{Z}Z} + \alpha_j I, \\
    \vect{\mu}_j &= \beta_j \Sigma_j \trans{\Ex{}{Z}} \vect{x}_j.
\end{align*}
Since the design matrix satisfies $Z_{ik} = \phi_k(z_i)$, we have
\[
    \Ex{}{\trans{Z}Z} = \sum_{i=1}^{N} \Ex{}{\phi(z_i) \trans{\phi(z_i)}}.
\]

Collecting the posterior means into a matrix gives
\[
    \Ex{}{W} = [ \vect{\mu}_1 \ \dots \ \vect{\mu}_M ].
\]
To simplify later expressions, define the diagonal precision matrix
\[
    B = \operatorname{diag}(\beta_1, \dots, \beta_M).
\]
Then, we have
\begin{align*}
    \sum_{j=1}^M \beta_j \Ex{}{\vect{w}_j \trans{\vect{w}_j}} &=
    \Ex{}{W} B \trans{\Ex{}{W}} + \sum_{j=1}^M \beta_j \Sigma_j.
\end{align*}
This quantity will appear in the update for the latent variables.
Note that if $\alpha_j = 0$ for all $j$, the mean simplifies to
\[
    \Ex{}{W} =  \Ex{}{\trans{Z}Z}^{-1} \trans{\Ex{}{Z}} X.
\]

We now consider the update equation for the factor $q(\mu, \tau)$:
\begin{align*}
    \ln q^*(\mu, \tau)
    &= \Ex{q(\vect{z})}{ \ln p(\mu, \tau \mid \vect{z}) } + \text{const} \\
    &= - \frac{\tau}{2} \left(\sum_{i} \Ex{}{z_i^2} - 2\mu \sum_{i} \Ex{}{z_i} + N\mu^2 \right) \\
    &\quad + \left(\frac{N}{2}-1\right)\ln\tau  + \text{const}.
\end{align*}
We define
\begin{align*}
    \avgz &= \frac{1}{N} \sum_i \Ex{}{z_i}, \\
    \avgzz &= \frac{1}{N} \sum_i \Ex{}{z_i^2}.
\end{align*}
We observe that $q^*(\mu, \tau)$, for $N > 1$ follows a Normal–Inverse–Gamma distribution:
\begin{equation*}
    q^*(\mu, \tau) = \Nor{\mu}{\avgz}{\frac{1}{N \tau}} \Gam{\tau}{\hf[N-1]}{\hf[N](\avgzz - \avgz^{2})}.
\end{equation*}
This implies
\begin{align*}
    \Ex{}{\tau} &= \frac{(N - 1)}{N(\avgzz - \avgz^{2})}, \\
    \Ex{}{\mu \tau} &= \avgz \Ex{}{\tau}.
\end{align*}

Finally, we derive the update equation for $q(\vect{z})$:
\begin{align*}
    \ln q^*(\vect{z}) &= \Ex{q(W,\mu,\tau)}{\ln p(X \mid \vect{z}, W) +
    \ln p(\vect{z} \mid \mu, \tau)} + \text{const} \\
    &= \Ex{q(W)}{\ln p(X \mid \vect{z}, W)} +
    \Ex{q(\mu,\tau)}{\ln p(\vect{z} \mid \mu, \tau)} + \text{const}.
\end{align*}

We expand the terms $\ln p(X \mid \vect{z}, W)$ and $\ln p(\vect{z} \mid \mu, \tau)$.
All expressions that are independent of $\vect{z}$ are treated as constants.
\begin{align*}
    \ln p(X \mid \vect{z}, W)
    &= \sum_{j} \ln \mathcal{N} (\vect{x}_j \mid Z \vect{w}_j,  \beta_j^{-1}I) \\
    &= -\hf \sum_j \beta_j \normsq{Z\vect{w}_j - \vect{x}_j} + \text{const} \\
    &= \sum_{i} \left(-\hf \trans{\phi (z_i)} \sum_j \beta_j \vect{w}_j \trans{\vect{w}_j} \phi (z_i)  +
                    \trans{\phi(z_i)} \sum_j \beta_j X_{ij} \vect{w}_j \right) + \text{const}. \\ \\
    \ln p(\vect{z} \mid \mu, \tau) &= -\hf[\tau] \sum_i (z_i - \mu) ^ 2 + \text{const} \\
    &= \sum_i \left( -\hf[\tau] z_i^2 + \tau \mu z_i \right) + \text{const}.
\end{align*}
Substituting these expansions into the variational update expression and taking the expectation yields:
\begin{equation*}
    \ln q^*(\vect{z}) = \sum_i \ln q^*(z_i),
\end{equation*}
where
\begin{align*}
    \ln q^*(z_i) &=
    \left(-\hf \trans{\phi (z_i)} \sum_j \beta_j \Ex{}{\vect{w}_j \trans{\vect{w}_j}} \phi (z_i) +
        \trans{\phi (z_i)} \Ex{}{W} B \trans{X_{i,:}} \right) \\
    &\quad + \left( -\hf \Ex{}{\tau} z_i^2 + \Ex{}{\tau \mu} z_i \right)
    + \text{const}.
\end{align*}
Here $X_{i,:}$ denotes the $i$-th row of the observation matrix $X$.

Because the update expression separates as a sum over
$i$, the optimal factor $q(\vect{z})$ factorizes as $\prod_i q(z_i)$.
Define
\begin{align*}
    S^{-1} &= \sum_j \beta_j \Ex{}{\vect{w}_j \trans{\vect{w}_j}}, \\
    \vect{m}_i &= S \Ex{}{W} B \trans{X_{i,:}}\,.
\end{align*}
Then, up to normalization,
\begin{equation*}
    q^*(z_i) \propto
    \Nor{\phi(z_i)}{\vect{m}_i}{S}
    \Nor{z_i}{\Ex{}{\mu}}{\Ex{}{\tau}^{-1}}.
\end{equation*}
Note that since the basis mapping is nonlinear,
this does not generally imply that $q^*(z_i)$ is Gaussian in $z_i$.

As seen previously, the update equations require expectations of the form
\begin{equation*}
    \Ex{}{\phi_i(z_k)\phi_j(z_k)}, \quad
    \Ex{}{\phi_i(z_k)}, \quad
    \Ex{}{z_k}, \quad
    \Ex{}{z_k^2},
\end{equation*}
for all relevant indices $i,j,k$.
These expectations typically do not admit closed forms and must be approximated numerically.