\newcommandx{\engFunc}[2][1=Q, 2=P]{\measure{F}{}{#1,\tilde{#2}}}
\newcommand{\infR}{\inf_{\inSet{R}}}
\newcommand{\supR}{\sup_{\inSet{R}}}

Suppose we want to approximate a central distribution of a hierarchy of distributions~\set{h}.
To do so, we need a measure that quantifies the quality of an approximation.
A natural choice is the central divergence introduced in Definition~\ref{def:central-divergence}.
Since central distributions are intended to serve as representatives of hierarchies of distributions,
central divergence can be viewed as a measure of how well a probability distribution represents a hierarchy.

At first glance, computing this quantity appears to require explicit knowledge of the central distributions of~\set{h}.
However, it turns out that the central divergence admits an upper bound that can be estimated without explicitly
knowing the central distribution.

In variational settings, it is often more convenient to work with unnormalized measures rather than normalized
distributions.
Therefore, we state the next theorem in terms of unnormalized measures.

\begin{theorem}\label{th:central-approx}
    Let \setQ be a finite set of probability distributions over a discrete random variable~$X$.
    Let $\tilde{P}$ be a positive measure over $X$,
    and let $P$ be the corresponding normalized distribution.
    Let $R$ be an arbitrary convex combination of the elements of $\set{R} \subseteq \setQ$.
    Then
    \[
        \myDiv[P][Q][] \leq \supR \engFunc - \inf_{\inSet{Q}} \engFunc + \kl[R][P],
    \]
    where
    \[
        \engFunc = \entropy{Q}{X} + \Ex{Q}{\ln \tilde{P}(X)}.
    \]
\end{theorem}

\begin{proof}
    By Corollary~\ref{cor:cdiv-lambda-bound}, we have
    \[
        \myDiv[P][Q][] \leq \sFunc[][\setQ] - g(\cDist).
    \]
    where \cDist is the \cd.

    Since $R$ is a convex combination of the elements of \set{R}, Lemma~\ref{lm:kl-bound} implies
    \[
        g(R) \geq \infR \kl - \kl[R][P].
    \]
    By Theorem~\ref{th:C-maximizes-g}, \cDist is a maximizer of $g$, and therefore
    \[
        g(\cDist) \geq g(R).
    \]
    Combining these three inequalities yields
    \begin{equation} \label{eq:cdiv-upper-bound}
        \myDiv[P][Q][]  \leq \sFunc[][\setQ] - \infR \kl + \kl[R][P].
    \end{equation}

    Let $\tilde{P}(X) = Z P(X)$, where $Z > 0$ is a normalization constant.
    Then for any~$Q$,
    \[
        \kl = \ln Z - \engFunc.
    \]
    Since $\ln Z$ does not depend on $Q$, we have
    \begin{align*}
        \infR \kl &= \ln Z - \supR \engFunc \\
        \sup_{\inSet{Q}} \kl &= \ln Z - \inf_{\inSet{Q}} \engFunc,
    \end{align*}
    and the result follows from Equation~\ref{eq:cdiv-upper-bound}.
\end{proof}

To compute an approximate central distribution, Theorem~\ref{th:central-approx} suggests constructing a positive
measure $\tilde P$ for which $\engFunc$ is approximately constant over \setQ.
We may choose this constant to be zero and seek
\[
    \engFunc \approx 0.
\]
In addition, the normalized distribution $P$ should be close enough to a convex combination of the elements of \setQ.

Since central distributions are defined through marginal distributions, their construction may be viewed as
combining prior specification and Bayesian inference within a single optimization framework.
Given $n$ observations, one may perform inference using the central distribution of the corresponding finite
sequence~$S_n$, without separately specifying a prior distribution.

For sequences of random variables, however, central distributions are defined on the
underlying infinite sequence.
Consequently, the central distribution of a finite initial segment $S_n$ should be viewed as an approximation to the
corresponding marginal of the infinite-sequence central distribution.
The question then becomes how accurate this approximation is.

One approach to computing an approximate central distribution is to represent $\ln \tilde P(X)$ as a linear
combination of a suitable set of basis functions,
analogous to the log-density representation used in exponential families:
\[
    \ln \tilde P(x) = -\sum_i \alpha_i b_i(x).
\]
Substituting this into $\measure{F}{}{}$ gives
\[
    \engFunc = \entropy{Q}{X} - \sum_i \alpha_i \Ex{Q}{b_i(X)}.
\]
Therefore, enforcing $\engFunc \approx 0$ amounts to approximating the entropy function by a linear
combination of the feature expectations $\Ex{Q}{b_i(X)}$.

Suppose that \setQ is indexed by a parameter \param.
We may then choose the coefficients $\alpha_i$ so that for every \paramVal
\[
    \sum_i \alpha_i \Ex{}{b_i(X) \mid \paramVal} \approx \entropy{Q}{X \mid \paramVal},
\]
and the resulting probability distribution is given by
\[
    P(x) \propto \exp \left\{-\sum_i \alpha_i b_i(x) \right\}.
\]

It should be noted that the quality of the approximation depends on how well $\tilde P$ can be represented as a
nonnegative linear combination of distributions \inSet[Q_{\paramVal}]{Q}.
This can be assessed approximately using a sample set of parameter values \set{S} by finding nonnegative weights $w_i$
such that
\[
    \tilde P(x) \approx \sum_i w_i Q(x \mid \paramVal_i),
\]
where $\inSet[\paramVal_i]{S}$.

The following example illustrates the approximation procedure in a simple binomial setting.

\begin{example}
    \input{approx_example}
\end{example}