A natural application of hierarchical central distributions arises in feature selection.
When the relevant set of features is unknown, each candidate feature set induces a distinct family of admissible
distributions.
Feature selection can therefore be viewed as uncertainty over a hierarchy of probabilistic models, making it a
natural setting for the central distribution framework.

To illustrate this idea, we provide a proof of concept experiment using synthetic data.
The purpose of this section is not to establish a competitive feature selection procedure, but to illustrate how
hierarchical central distributions can be used to represent uncertainty over model structure.
A comprehensive empirical evaluation against established feature selection methods, such as Spike-and-Slab priors,
on real-world datasets lies beyond the scope of this foundational paper and is left for future work.

We consider a classification problem where the goal is to
predict a target class, denoted by $Y$, from a set of observed nominal attributes $(\seqExp{A})$.
We assume that $Y$ may depend on an unknown subset of the attributes, rather than the full set.

To capture this relationship, we use the fused multinomial model introduced in Example~\ref{ex:fused-multinomial}.
As an example, assume that $Y$ depends only on $A_2$ and $A_5$.
Then, we define the labeling function $f$ as follows:
\[
    f(\seqExp{A}, Y) = (A_2, A_5, Y).
\]
In a fused multinomial model with this labeling function, the target class $Y$ is conditionally independent of
all other attributes given $A_2, A_5$.

For every possible subset of attributes, a distinct fused multinomial model of this form is constructed.
Each such model corresponds to a set of plausible probability distributions.
Collecting these sets yields our overall uncertainty representation, which forms a one-level
hierarchy of distributions (Definition~\ref{def:hierarchy-of-distributions}).

Let $C_{\setQQ}$ denote a central distribution of the full hierarchy, and let $C_{f_i}$ denote the central
distribution of the fused multinomial model associated with the labeling function $f_i$.
As discussed earlier, because the number of candidate models is finite, we have
\begin{equation}\label{eq:att-select-central}
    C_{\setQQ}(S_n) \propto \sum_i C_{f_i}(S_n).
\end{equation}

To justify this, observe that we can construct a consistent estimator for the model indicator $I$ by examining
equality relationships among the observed frequencies of outcomes.
Specifically, the estimator identifies outcomes that occur with equal frequencies and returns the
indicator corresponding to the model that supports those equalities.

The optimal Bayesian decision rule depends on the choice of loss function.
In this example, we use the zero--one loss, under which the optimal strategy predicts the target class with the highest
posterior probability.
These posterior probabilities are computed using the central distribution of Equation~\ref{eq:att-select-central}.
It turns out that each subset-specific fused multinomial model is assigned its corresponding
Jeffreys' prior.
Consequently, the resulting predictive distribution can be interpreted as Bayesian model averaging over all
candidate feature subsets, with each model equipped with its Jeffreys' prior.
The central distribution framework provides a principled minimax-KL interpretation of this aggregation.

To see how this approach works in practice, we carried out a synthetic experiment with the following setup.
We considered binary attributes and generated each attribute independently with equal probability for 0 and 1.
The target class was defined as a deterministic function of a fixed subset of 3 out of 12 total attributes, as
shown in Table~\ref{tab:functions}.
The same subset of relevant attributes and class assignment function were used across all trials.

\begin{table}[tb]
    \centering
    \caption{Mappings of 3-bit inputs under class functions $Y_1$ and $Y_2$}
    \begin{tabular}{ccc}
        \toprule
        Input (bits) & $Y_1$(Input) & $Y_2$(Input) \\
        \midrule
        000          & a            & A            \\
        001          & b            & B            \\
        010          & c            & A            \\
        011          & d            & C            \\
        100          & e            & D            \\
        101          & f            & D            \\
        110          & g            & D            \\
        111          & h            & E            \\
        \bottomrule
    \end{tabular}\label{tab:functions}
\end{table}

For each experiment, we generated a test set of size 100.
A larger test set was used to reduce variability in performance estimates, taking advantage of the synthetic
nature of the data.
To assess robustness to irrelevant features, we progressively removed one attribute at a time from the full set
of 12, starting with irrelevant ones and stopping just before removing any of the three relevant attributes.

At each step, we trained and tested two versions of the central distribution: one assuming that the target class is
a deterministic function of the attributes (CD-Det), and one allowing the target class to follow a conditional
probability distribution given the attributes (CD-Prob).
Both versions are constructed by aggregating over $2^{12}$ fused multinomial models, corresponding to all subsets of
the 12 attributes.
As a baseline, we also trained a decision tree classifier (D-Tree).
All methods were trained on the same training data and evaluated on the same test data.
Each configuration was repeated for 100 independent trials, and we reported the average accuracy (correct
predictions divided by total test instances) over these trials.

\begin{figure}[t]
    \centering
    \begin{tikzpicture}
        \begin{axis}[
            globalstyle,
            xlabel={Number of Attributes},
            ylabel={Accuracy},
            xmin=3, xmax=12,
            ymin=0.0, ymax=1.0,
            xtick={3,...,12},
        %ytick={0.0, 0.3, 0.6, 0.9},
        ]

            \addplot+[mark=*, blue] coordinates {
                (3, 0.939) (4, 0.939) (5, 0.939) (6, 0.9381) (7, 0.9344) (8, 0.9321) (9, 0.9286) (10, 0.9275) (11, 0.9273) (12, 0.9245)
            };
            \addlegendentry{CD-Det}

            \addplot+[mark=square*, red] coordinates {
                (3, 0.9271) (4, 0.9271) (5, 0.9271) (6, 0.9271) (7, 0.9271) (8, 0.9271) (9, 0.9271) (10, 0.9271) (11, 0.9271) (12, 0.9244)
            };
            \addlegendentry{CD-Prob}

            \addplot+[mark=triangle*, black] coordinates {
                (3, 0.1885) (4, 0.1881) (5, 0.19) (6, 0.189) (7, 0.188) (8, 0.1883) (9, 0.1869) (10, 0.1862) (11, 0.1864) (12, 0.1855)
            };
            \addlegendentry{D-Tree}

        \end{axis}
    \end{tikzpicture}
    \begin{tikzpicture}
        \begin{axis}[
            globalstyle,
            xlabel={Number of Attributes},
            xmin=3, xmax=12,
            ymin=0.0, ymax=1.0,
            xtick={3,...,12},
        %ytick={0.3,0.6,0.9},,
        ]

            % --- CD-Det ---
            \addplot+[blue, mark=*, line width=0.9pt] coordinates {
                (3, 0.9455) (4, 0.9407) (5, 0.9378) (6, 0.9403) (7, 0.9424) (8, 0.9432) (9, 0.9418) (10, 0.9376) (11, 0.9321) (12, 0.9209)
            };
            \addlegendentry{CD-Det}

            % --- CD-Prob ---
            \addplot+[red, mark=square*, line width=0.9pt] coordinates {
                (3, 0.8447) (4, 0.8419) (5, 0.8402) (6, 0.8337) (7, 0.8313) (8, 0.8288) (9, 0.8296) (10, 0.825) (11, 0.8227) (12, 0.817)
            };
            \addlegendentry{CD-Prob}

            % --- D-Tree ---
            \addplot+[black, mark=triangle*, line width=0.9pt] coordinates {
                (3, 0.3685) (4, 0.3668) (5, 0.3609) (6, 0.3589) (7, 0.358) (8, 0.357) (9, 0.3571) (10, 0.3545) (11, 0.3528) (12, 0.3516)
            };
            \addlegendentry{D-Tree}

        \end{axis}
    \end{tikzpicture}
    \caption{
        Accuracy versus number of attributes for 20 training samples.
        Left: under class assignment function $Y_1$.
        Right: under class assignment function $Y_2$.
    }
    \label{fig:f1-f2-results}
\end{figure}

The results, presented in Figure~\ref{fig:f1-f2-results}, show that both central distribution
methods substantially outperform the decision tree on the two classification tasks.
Interestingly, the relative difficulty of the tasks differs between the methods.
For the central distribution approach, $Y_2$ is more challenging than $Y_1$, resulting in a larger gap between the
deterministic and probabilistic variants.
This difficulty arises from strong non-deterministic dependencies between subsets of input bits and the assigned
class, which can create misleading probabilistic associations.
In contrast, the decision tree performs worse on $Y_1$ than on $Y_2$.
Overall, the deterministic central distribution achieved the highest accuracy, while the probabilistic version
produced similar but slightly weaker results.

\begin{figure}[t]
    \centering
    \begin{tikzpicture}
        \begin{axis}[
            globalstyle,
            xlabel={Number of Attributes},
            ylabel={Accuracy},
            xmin=3, xmax=12,
            ymin=0.4, ymax=0.8,
            xtick={3,...,12},
        ]

            \addplot+[mark=*, blue] coordinates {
                (3, 0.7446) (4, 0.7342) (5, 0.7229) (6, 0.7111) (7, 0.6946) (8, 0.6772) (9, 0.6613) (10, 0.6398) (11, 0.6174) (12, 0.5993)
            };
            \addlegendentry{CD-Det}

            \addplot+[mark=square*, red] coordinates {
                (3, 0.7068) (4, 0.695) (5, 0.6765) (6, 0.6394) (7, 0.599) (8, 0.5672) (9, 0.5368) (10, 0.51) (11, 0.4829) (12, 0.4584)
            };
            \addlegendentry{CD-Prob}

        \end{axis}
    \end{tikzpicture}
    \begin{tikzpicture}
        \begin{axis}[
            globalstyle,
            xlabel={Number of Attributes},
            xmin=3, xmax=12,
            ymin=0.4, ymax=0.8,
            xtick={3,...,12},
        ]

            \addplot+[mark=*, blue] coordinates {
                (3, 0.7634) (4, 0.7535) (5, 0.7337) (6, 0.7272) (7, 0.7092) (8, 0.6913) (9, 0.6856) (10, 0.6709) (11, 0.6556) (12, 0.6378)
            };
            \addlegendentry{CD-Det}

            \addplot+[mark=square*, red] coordinates {
                (3, 0.736) (4, 0.7184) (5, 0.7063) (6, 0.6991) (7, 0.6849) (8, 0.6692) (9, 0.656) (10, 0.6397) (11, 0.6214) (12, 0.6047)
            };
            \addlegendentry{CD-Prob}

        \end{axis}
    \end{tikzpicture}
    \caption{
        Accuracy versus number of attributes for 10 training samples.
        Left: under class assignment function $Y_1$.
        Right: under class assignment function $Y_2$.}
    \label{fig:f1-f2-10samples-results}
\end{figure}

With 20 training samples, removing irrelevant attributes had little effect on performance.
Accuracy remained nearly constant as the number of attributes decreased from 12 to 3, and the decision tree showed a
similar insensitivity to attribute count.
However, with only 10 training samples (Figure~\ref{fig:f1-f2-10samples-results}),
accuracy increased noticeably as irrelevant attributes were removed, indicating that irrelevant
features become more problematic in low-data regimes.

The implementation used in this experiment evaluates all $2^{12}$ candidate feature subsets and therefore remains
computationally feasible only because the dimensionality is small.
More generally, because the central distribution aggregates over all candidate subsets, the resulting predictor is
not expected to scale to high-dimensional problems without additional approximation techniques.
Developing scalable approximation methods could be a direction for future work.



