\newcommandx{\supD}[3][1=P, 2=\setQ, 3=X]{\sup_{Q \in #2} \kl[Q][#1][#3]}
\newcommand{\argSupD}[1][\setQ]{\arg\min_{P}\sup_{Q \in #1}}
\newcommand{\myDiv}[1][P(X)]{\measure{D}{\mathrm{CD}}{\set{H} \,\middle\|\, #1}}
\newcommandx{\klExp}[3][1=Q, 2=P, 3=x]{\sum_{#3} #1(#3) \ln \frac{#1(#3)}{#2(#3)}}
\newcommand{\inSet}[1]{\mathFix{#1 \in \set{#1}}}

\newcommand{\saddle}{\mathFix{(\saddP, \saddR)}}
\newcommand{\fExp}{\sum_i R(i) \klExp[Q_i]}
\newcommand{\cDist}[1][]{\mathFix{\sub{C}{#1}}}
\newcommand{\ccDist}[1][]{\mathFix{\sub{C^{*}}{#1}}}
\newcommand{\cPrior}{\mathFix{c}}
\newcommand{\like}{Q}
\newcommand{\sadd}[1]{\mathFix{#1^{*}}}
\newcommand{\saddR}{\sadd{R}}
\newcommand{\saddP}{\sadd{P}}
\newcommand{\est}{T}

\newcommand{\fun}[1][]{\ifthenelse{\isempty{#1}}{}{(#1)}}

Consider a random variable $X$.
In probabilistic modeling, our knowledge about
$X$ is represented by a probability distribution, which serves as a basis for making inferences.

However, in many situations, our information may be too limited to justify choosing a single distribution.
Instead, we may only be able to specify a set of plausible distributions.
Such a set represents some form of \emph{uncertainty} or \emph{partial knowledge}: although it does not identify a
single distribution, it constrains the range of plausible probabilistic models.

A well-known example of this idea is the exchangeability assumption used in de Finetti’s theorem.
A sequence of random variables \infSeqExp{X} is said to be exchangeable, if the ordering of the variables carries no
information.
That is, the joint probability distribution remains invariant under permutations of the variables.
This assumption imposes a constraint, effectively introducing a set of plausible distributions.
Thus, exchangeability can be seen as a specific form of partial knowledge.

In this work, we adopt the view that a set of probability distributions can represent a meaningful state of partial
knowledge, and that such set-valued uncertainty may itself be used as the basis for inference.

More generally, partial knowledge may possess a hierarchical structure.
In the simplest case, uncertainty is represented by a single set of candidate distributions.
In richer settings, however, this uncertainty may be organized into nested collections, where elements of a set may
themselves be sets of distributions.
Such nesting can continue recursively, yielding a hierarchical uncertainty structure.

Crucially, the choice of hierarchical organization is itself informative: grouping distributions into subsets
expresses that certain alternatives are regarded as belonging to a common epistemic category and should therefore be
aggregated before being compared with alternatives in other groups.
Consequently, the hierarchy encodes information beyond the collection of leaf distributions alone.

This hierarchical organization may be interpreted as introducing multiple layers of latent structural decisions,
where higher-level choices restrict the admissible lower-level alternatives.

Within a Bayesian framework, inference ultimately requires a single probability measure.
Therefore, to use hierarchical partial knowledge in Bayesian inference, we require a principled method for
transforming a nested set-valued uncertainty representation into a single probability distribution while preserving
the informational structure encoded by the hierarchy.

We adopt the principle that the probability measure used to represent prior beliefs about the environment should
depend only on the available information about the environment itself, and not on agent specific considerations such as
the loss function or the informativeness of observations.
We refer to this modeling assumption as \emph{the principle of objectivity}.

From a minimax perspective, when uncertainty is represented by a set of candidate distributions, a natural
representative distribution is one that minimizes the worst-case divergence to the members of the set.
Such a distribution may be viewed as the most conservative or robust single-distribution summary of the available
partial knowledge.

\begin{definition}[Central Distribution]
    Let $X$ be a random variable and \setQ be a set of probability distributions over $X$.
    We say a distribution $C$ is a \emph{central distribution} of \setQ for $X$, if for every probability
    distribution $P$, we have
    \begin{equation}
        \supD[\cDist] \leq \supD[P],
        \label{eq:central-def}
    \end{equation}
    where $\measure{D}{\mathrm{KL}}{}$ denotes the Kullback–Leibler (KL) divergence.
\end{definition}

Note that, under this definition, the central distribution of \setQ is not necessarily an element of \setQ.
That is, the distribution that best represents the set in the specified sense may lie outside the set it summarizes.

Sometimes partial knowledge is represented by a hierarchical structure of sets of distributions.
Our current definition of the central distribution does not account for this case.
The following recursive definitions extend the concept to handle such situations.
While not directly about feature selection, this extension plays a key role in enabling the connection between
central distributions and feature selection, a connection that will become clearer later.

\begin{definition}[Hierarchy of Distributions]
    A \emph{hierarchy of distributions} over $X$ is defined recursively as follows:
    \begin{itemize}
        \item Any set of probability distributions over $X$ is a hierarchy of distributions over $X$.
        \item Any set whose elements are hierarchies of distributions over $X$ is itself a hierarchy of
        distributions over $X$.
    \end{itemize}
\end{definition}

Intuitively, a central distribution acts as a representative or summary of a set of distributions.
While it may not belong to the set itself, it reflects the overall behavior of the set in a way that is meaningful
for inference and also induces a notion of divergence for evaluating probability distributions under partial
knowledge.

The concept of a central distribution is not intended to yield a unique object; rather, all distributions satisfying
the definition can be regarded as equally good representatives.
However, when multiple central distributions exist, our constructions should not depend on an arbitrary
choice among them.
To avoid such dependence, we define the central divergence using the best divergence attained over the set of all
central distributions.

\begin{definition}[Central Divergence]
    \label{def:central-divergence}
    For any distribution $P$, we define the \emph{central divergence} of $P$ from a hierarchy of distributions \set{H},
    with respect to a random variable $X$, as follows:
    \begin{equation*}
        \myDiv = \inf_{\cDist} \kl[{\cDist}],
    \end{equation*}
    where $\cDist$ denotes a central distribution of \set{H} for $X$.
\end{definition}

So far, this definition applies only when the hierarchy is a single set of distributions.
The following definition extends the construction recursively to general hierarchical uncertainty structures.

\begin{definition}
    \label{def:hierarchy-of-distributions}
    Let $X$ be a random variable, and let \set{H^*} be a hierarchy of distributions over $X$ whose elements are
    hierarchies of distributions.
    We say \ccDist is a central distribution of \set{H^*}, if for every probability distribution $P$ we have:
    \begin{equation*}
        \sup_{\set{H} \in \set{H^*}} \myDiv[\ccDist(X)]  \leq \sup_{\set{H} \in \set{H^*}} \myDiv,
    \end{equation*}
    where $\myDiv[\none]$ refers to the central divergence as defined in Definition~\ref{def:central-divergence}.
\end{definition}

A simple example illustrates that hierarchical organization can affect the resulting representative distribution
even when the underlying admissible sets remain unchanged.

Let \(X\) be a random variable with three possible outcomes \(x_1,x_2,x_3\).
For each \(i\), let \(S_i\) denote the set of all probability distributions over \(X\) that assign zero probability to \(x_i\).

By symmetry, the central distribution of each set \(S_i\) is the uniform distribution over its support:
\[
    C_{S_1}=\left(0,\frac12,\frac12\right),\qquad
    C_{S_2}=\left(\frac12,0,\frac12\right),\qquad
    C_{S_3}=\left(\frac12,\frac12,0\right).
\]

If the three sets \(S_1,S_2,S_3\) are treated symmetrically as elements of a single set, then their central
distribution is
\[
    C_{\{S_1,S_2,S_3\}}=
    \left(\frac13,\frac13,\frac13\right).
\]

Now consider instead a hierarchical organization in which \(S_1\) and \(S_2\) are grouped together, while \(S_3\)
forms its own separate branch.

Taking the central distribution of these two representatives yields
\begin{align*}
    C_{\{\{S_1,S_2\}, S_3\}}
    &= \frac12 C_{\{S_1,S_2\}} + \frac12 C_{S_3} \\
    &= \frac14 C_{S_1} + \frac14 C_{S_2} + \frac12 C_{S_3} \\
    &= \left(\frac38,\frac38,\frac14\right).
\end{align*}

Thus, although the underlying admissible sets are identical in both constructions, the resulting representative
distribution differs.

This demonstrates that hierarchical structure carries informational content beyond the collection of leaf sets
alone.
Consequently, flattening a hierarchy into a single unstructured set may discard meaningful epistemic structure.

In many learning problems, uncertainty concerns not only the parameters of a predictive model but also its
structural form.
In particular, when the relevance of potential features is unknown, each candidate feature subset determines a
distinct set of distributions in which the target variable depends only on that feature subset.

Feature selection may therefore be viewed as uncertainty over a collection of distributions.
The hierarchical central distribution framework provides a natural mechanism for representing and aggregating such
uncertainty.
By organizing candidate features hierarchically, one may encode preferences over structural hypotheses, such as
favoring sparse subsets, grouping related attributes, or privileging particular interactions.

Candidate feature subsets typically induce overlapping families of admissible distributions.
Distributions exhibiting simpler dependency structure may belong simultaneously to many such families, whereas more
specific dependency patterns belong to fewer.
As a result, hierarchical aggregation through central distributions can induce a preference toward structurally
simpler models by assigning more weight to distributions compatible with multiple structural hypotheses.

With the notion of hierarchical central distributions established, we now develop the theoretical machinery needed
to characterize and compute them.
The following results provide optimization-theoretic characterizations of central distributions that form the
foundation of the subsequent analysis.

\begin{definition}[Interior Distribution]
    \label{def:interior}
    Let \setQ be a set of probability distributions over a random variable $X$.
    A distribution $R$ is called an \emph{interior distribution} of \setQ if, for every probability distribution $P$,
    there exists some $\inSet{Q}$ such that
    \begin{equation*}
        \kl[R] \leq \kl[Q],
    \end{equation*}
\end{definition}

\begin{theorem}
    Any distribution that can be expressed as a convex combination of elements of \setQ is an
    interior distribution of \setQ.
\end{theorem}

\begin{proof}
    Let $R = \sum_i \alpha_i Q_i$, where $Q_i \in \setQ$, $\alpha_i \geq 0$, and $\sum_i \alpha_i = 1$.

    Fix an arbitrary probability distribution $P$.
    By the convexity of KL divergence in its first argument, we have:
    \[
        \kl[R] \leq \sum_i \alpha_i \kl[Q_i] \cdot
    \]
    Now, note that the right-hand side is a weighted average of the KL divergences.
    So, there must be at least one index $j$ such that
    \[
        \kl[R] \leq \kl[Q_j] \cdot
    \]
    Since $Q_j \in \setQ$, the condition in Definition~\ref{def:interior} is satisfied,
    and $R$ is indeed an interior distribution of \setQ.
\end{proof}

\begin{theorem}
    Let $R$ be an interior distribution of \setQ.
    If $C$ is a central distribution of \setQ, it is also a central distribution of $\setQ \cup \{R\}$ and vice versa.
\end{theorem}

\begin{proof}
    This theorem follows directly from the definition of an interior distribution, which implies that for any
    probability distribution $P$, we have
    \[
        \supD = \supD[][\setQ \cup \{R\}] \cdot \qedhere
    \]
\end{proof}

One important consequence of this theorem is that, in order to identify a central distribution within a parametric
model, it suffices to restrict attention to the set of likelihood distributions induced by different values of the
model parameters.

The next theorem is a standard result that is typically used in the derivation of central distributions.

\begin{theorem}
    \label{th:estimator-to-var}
    Let $X$ and $T$ be two random variables, and let \setQ be a set of distributions over the pair $(X,T)$.
    Assume that for every \inSet{Q}, we have
    \[
        Q(X, T) = R(\XIT) Q(T),
    \]
    where $R$ is a fixed conditional distribution.
    If $C$ is a central distribution of \setQ for $T$, then $R(\XIT)C(T)$ is a central
    distribution of \setQ for $(X,T)$.
\end{theorem}

\begin{proof}
    Let $C$ be a central distribution of \setQ for $T$.
    For an arbitrary probability distribution $P$ we have
    \begin{equation}
        \label{eq:th5-proof}
        \sup_{Q \in \setQ} \Dkl{Q(X,T)}{R(\XIT) C(T)} \leq \sup_{Q \in \setQ} \Dkl{Q(X,T)}{R(\XIT) P(T)} \cdot
    \end{equation}

    Since the KL divergence is nonnegative, for every probability distribution $P$ and every \inSet{Q} we have
    \[
        \sum_t \Dkl{R(X \mid t)}{P(X \mid t)} Q(t) \geq 0.
    \]
    That implies
    \[
        \Dkl{Q(X,T)}{P(X,T)} - \Dkl{Q(X,T)}{R(\XIT) P(T)} \geq 0.
    \]
    Taking the supremum over \inSet{Q} preserves the inequality, since it holds pointwise for every \inSet{Q}:
    \[
        \sup_{Q \in \setQ} \Dkl{Q(X,T)}{R(\XIT) P(T)} \leq \sup_{Q \in \setQ} \Dkl{Q(X,T)}{P(X,T)} \cdot
    \]
    Combining this inequality with Inequality~\ref{eq:th5-proof}, we conclude that $R(\XIT)C(T)$ is a
    central distribution of \setQ for $(X,T)$.
\end{proof}


\input{minimax}

\input{infty}

\begin{example}[Fused Multinomial Model]
    \label{ex:fused-multinomial}
    \newcommand{\prodm}{\prod_{y=1}^m}
    \newcommand{\Qt}{Q_{\theta}}
    Let \infSeq{S} be a sequence where each $S_n = (\seqExp{X})$ represents $n$ independent trials of an
    experiment with $k$ possible outcomes,
    and \setQ be a set of probability distributions over $S_n$ indexed by a real vector \paramVal.
    Let $f: \set{X} \to \set{Y}$ be a deterministic function that maps each outcome of $X_i$
    to a label $Y_i = f(X_i)$, where $\set{Y} = \{1, \dots, m\}$.
    Assume that for all $i$ and $\Qt \in \setQ$, if $f(x_i) = f(x'_i)$ we have \[\Qt(\seqExp{x}) = \Qt(\seqExp{x'}).\]
    That is, the conditional distribution $\Qt(X_i \mid Y_i = y)$ is uniform over the preimage $f^{-1}(y)$.

    We can consider $\theta = (\theta_1, \dots, \theta_m)$ to be a probability vector over $\mathcal{Y}$,
    where each $\theta_y$ specifies the probability of observing label $y$.
    For a sequence $S_n$, let $n_y$ denote the number of times label $y \in \mathcal{Y}$ appears.
    Let $|f^{-1}(y)|$ denote the number of outcomes in $\mathcal{X}$ that are mapped to label $y$ by $f$.
    Then the probability of observing $S_n$ under $\Qt \in \setQ$, denoted $Q(S_n \mid \theta)$, is:
    \[
        Q(S_n \mid \theta) = \prodm \left( \frac{1}{|f^{-1}(y)|} \cdot \theta_y \right)^{n_y} \cdot
    \]

    Now, consider the estimator sequence $T_n = \frac{1}{n} \left( \seqExp[m]{n} \right)$, which is a consistent
    estimator for $\theta$.
    The conditional distribution $Q(S_n \mid T_n)$ is then given by:
    \[
        Q(S_n \mid T_n) = \frac{1}{n!} \prodm \frac{n_y!}{|f^{-1}(y)|^{n_y}} \cdot
    \]
    Note that this distribution is independent of $Q_\theta$.
    Therefore, by Theorem~\ref{th:estimator-to-var}, a central distribution for $S_n$ can be obtained from a central distribution
    for $T_n$.

    As $n \to \infty$, the distribution of $T_n$ converges to a multivariate Gaussian distribution.
    Using this fact and Equation~\ref{eq:central-limit}, we can determine a central prior for \infSeq{T}:
    \[
        c(\theta) \propto \prodm \theta_y^{-\hf}
    \]
    This is a Dirichlet prior and induces a Dirichlet-multinomial distribution for each $T_n$:
    \[
        C(T_n) = \frac{\gm{\hf[m]}\gm{n+1}}{\gm{n + \hf[m]}}
        \prodm \frac{\gm{n_y + \hf}}{\gm{\hf}\gm{n_y+1}} \cdot
    \]
    Note that here, $C$ denotes a central distribution for $T_\infty$, and $C(T_n)$ refers to the marginal
    distribution induced on $T_n$.

    By Theorem~\ref{th:estimator-to-var}, we can derive a central distribution for \infSeq{S}, which induces the
    following distribution over each $S_n$:
    \[
        C_f(S_n) = \frac{\gm{\hf[m]}}{\gm{n + \hf[m]}}
        \prodm \frac{\gm{n_y + \hf}}{\gm{\hf} |f^{-1}(y)|^{n_y}} \cdot
    \]
\end{example}
