%    Notation:
%    \begin{itemize}
%        \item Random variable \rv{x} with value \rval{x} and possible values from $\range{x}$,
%        \item Random vector \rvec{x} with range $\vrange{x}$ and some assignment \vval{x},
%        \item Set \set{A}, and a measure \measure{M}.
%    \end{itemize}

\newcommand{\util}[1][{\rval[]{a}}]{U(#1, \rval[]{x})}
\newcommand{\envDist}{P^*}
\newcommand{\post}{\pi(\rval[i]{x} \mid \paramValue)}

We begin by revisiting a fundamental decision-making problem, and how it is treated within the framework of Bayesian
decision theory.

Consider an environment where an agent must select an action from a set of available actions.
The utility of each action for the agent depends on the unknown state of the environment, and can be quantified by a
real number.
Specifically, let \rval[]{a} denote an action, and \rval[]{x} represent the unknown environment state.
The utility function  $\util$ quantifies the desirability of each action.

Moreover, an evidence \rval[]{e} of this unknown environment state exists, and the agent can leverage this
evidence to determine the best action.
In other words, our agent aims to find the optimal strategy, where a strategy defines the distribution of each
action conditioned on the observed evidence.

According to Bayesian decision theory, the optimal strategy is the one that maximizes the expected utility:
\begin{equation*}
    S_{\text{opt}} = \arg\max_S\sum_a\sum_{x,e} \util S(a \mid e)\envDist(x, e).
\end{equation*}

Here, $\envDist(\XE)$ is the joint probability distribution of the environment state and the evidence.
However, a fundamental question arises: How do we obtain this distribution?
Is there an objective distribution inherent in the environment that we need to somehow discover?

Answering this question is not straightforward.
From a subjective perspective on probability, the answer is negative.
There is no such objective distribution, and $\envDist$ exists only in our minds.
It serves as a tool that helps us regulate our reasoning---an intermediate measure created within the
Bayesian decision-making framework to ensure we stay consistent with our assumptions and common sense principles.

Considering the subjective viewpoint, the determination of $\envDist$ relies on one’s prior knowledge and
assumptions.
When we have no assumptions and no prior knowledge, the set of candidate probabilities for $\envDist$ simply
consists of all possible probability measures.
As we make assumptions or obtain some prior knowledge, those probability measures that do not align
with our assumptions or knowledge are eliminated from this set.
Consequently, the set of acceptable probability measures becomes more refined.
We refer to this refined set as a probabilistic model:

\begin{definition}[Probabilistic Model]
    We define a \emph{probabilistic model} \M as a pair $\left(\set{S}, \set{P}\right)$, where \set{S} is a sample
    space, and \set{P} is a set of acceptable probability measures on \set{S}.
\end{definition}

One of the most commonly used assumptions of this kind in the statistical modeling is the exchangeability assumption.
We say a sequence of random variables $\seqRvInf$ is exchangeable if the ordering of variables does not provide any
useful information.
Or in other words, for an exchangeable sequence of random variables, the joint probability is the same
for any permutation of variables.
This property holds true for every subset of the sequence.

For example, if each \rv[i]{x} represents a binary variable, the joint probability depends solely on the total count
of 1s and 0s, and the specific order in which these variables appear becomes irrelevant.

When a sequence of random variables is exchangeable, de Finetti's theorem states that their joint probability has a
special representation:
\begin{equation*}
    P(\seqRvalInf) = \int \prod_i\post \dt.
\end{equation*}
This means, exchangeable observations are conditionally independent relative to some latent parameter $\paramValue$.

Moreover, the theorem states that if each \rv[i]{x} is discrete, the distribution $\post$ corresponds to the multinomial
distribution.


\begin{definition}[Parametric Model]
    \label{def:param-model}
    Let $\param$ be a random variable.
    A \emph{parametric model} is a probabilistic model \pmodel, where for every $P \in \set{P}$ there is a prior
    probability
    distribution $p$, such that for every $\rval[]{s} \in \set{s}$
    \begin{equation}
        \paramDist{\rval[]{s}},
        \label{eq:parametric}
    \end{equation}
    while $\pi$ is a fixed, known probability distribution.
    We refer to $\pi$ as the \emph{likelihood} distribution.
\end{definition}

Now, consider our decision-making problem: Suppose the evidence \rval[]{e} consists of a sequence of previous experiences
of the environment.
If we assume that our environment remains unchanged over time so that this sequence is exchangeable,
to fully determine $\envDist$, we only need to determine the prior distribution of the latent parameter $\prior$.

Clearly, one approach to selecting a suitable prior distribution $\prior$ is to rely on our prior knowledge about the
environment.
But what if such knowledge is unavailable?
Finding an answer is not simple.
In Bayesian statistics, this is where non-informative priors come into play.
These priors are typically chosen to be uniform or to represent a state of ignorance about the parameters.
However, these priors are not always ideal and can sometimes lead to misleading results.

Even when we have no prior knowledge, it is not difficult to identify some distributions that are not suitable
choices for $\prior$.
For instance, any distribution that assigns zero probabilities to certain values of $\paramValue$ is not a good choice.
If we use such a prior, no evidence can convince us that the value of $\paramValue$ lies within those
excluded values.

We cannot assert objectively that there is some type of underlying process in the environment for generating different
values of \paramValue that does not assign zero probability to any value of \paramValue.
Here, our argument is subjective.
We consider some priors to be unsafe because they have some characteristics that appear to be problematic:
in the obtained posterior, some values of the parameter are excluded regardless of the evidence.

We can generalize this idea and use a similar subjective approach to determine a somewhat “safe”
prior probability.
Recall that our probabilistic model for the environment consists of a set of acceptable probability measures \set{P}.
Suppose that we choose a probability measure $C \in \set{P}$, and determine the optimal Bayesian strategy in $C$.
If the expected utility of this strategy in any other probability measure
$P \in \set{P}$ is close to the optimal strategy, we can say that using $C$ is safe, in the
sense that the optimal strategy obtained using $C$, is a near optimal strategy in any other acceptable probability
measure in our model.
Interestingly, this relates closely to the concept of Bayesian convergence, where the posterior probability converges
to the same distribution regardless of the prior distribution.

The probability measure that we choose represents our beliefs about the environment.
This choice should not depend on our utility function, otherwise our beliefs about the environment would be a
function of our benefits.

Unfortunately, the expected utility of a strategy is a functional of the utility function.
Therefore, we cannot directly use the expected utility of the optimal Bayesian strategy for evaluating
different probability measures.
We need a measure that quantifies the similarity between two probability measures while it ignores the
specific utility function we are using.

Additionally, there is another factor that can help us choose the appropriate probability measure from our model.
Suppose that, instead of \rv{E}, we decide to use a different evidence, denoted as \rv{E'}.
Could this change potentially improve our strategy?
Within the framework of Bayesian decision theory, we can straightforwardly answer this question.
To compare any two strategies, we can simply compare their expected utilities.
The strategy with the greater expected utility is the better one.

Note that in reality we cannot freely choose any evidence we want.
The availability of evidence depends on the environment.
We can only choose evidence that is a function of the evidence provided by the environment,
allowing us to determine its value after observing the original evidence.
Utilizing a strategy that uses a simpler evidence, resembles feature selection in machine learning.
For instance, in a learning task where our evidence is an image, we might substitute the image with the first
three coefficients of its Fourier transform.
Naturally, these coefficients are a function of the original evidence.

Interestingly, if we assume $\rv{E'} = f(\rv{E})$, it turns out
that, according to our Bayesian framework, the optimal strategy for \rv{E} is always
better than any strategy that uses \rv{E'}.
Thus, at first glance, it appears that Bayesian decision theory does not favor feature selection.

In practice, we have to use feature selection because without it the original learning task requires
impractical large datasets.
From a certain perspective, it could be argued that adopting a strategy which uses simpler evidence may lead to
ignoring some parts of useful available information, and therefore can not be justified by Bayesian
decision theory.

The key point here is that the space of strategies using \rv{E'} is a subset of strategies that use \rv{E}.
When we are searching for the best strategy based on \rv{E}, we are implicitly evaluating all simpler forms as well.
Hence, we believe if we choose an appropriate probability measure $\envDist$, feature selection should
be performed automatically within the Bayesian framework when we are finding the optimal strategy.

Recall that, in parametric models (Definition~\ref{def:param-model}), choosing the probability measure $\envDist$ is
equivalent to choosing a prior distribution for the model parameter.
In Bayesian statistics when there is no prior knowledge we use non-informative priors.
However, many commonly used non-informative priors, such as the flat prior, do not exhibit feature
selection characteristics.

This seems to come from the fact that when we use these priors, in the resulted probability measure the estimate for
the distribution of $\XIE'$ differs from what we intuitively estimate.
This estimate tends to have a much higher entropy.
As a result the optimal strategy for \rv{E'} is mostly ignored because for any value of the evidence it yields a
poor expected utility.

It is reasonable to consider that if we find a probability measure which has a closer estimate to our
intuitive estimate for $\XIE'$ distribution, automatic feature selection will be performed within the Bayesian
framework.
We believe that can be done by using a probability measure that is “safe” for $\XIE'$, in the sense we just described.

Throughout this discussion, we will further investigate this idea and try to formulate a systematic approach to
determine such probability measures.
