\renewcommand{\t}{\paramValue}
\newcommand{\mdim}{d}
\newcommand{\msize}{n}
\newcommand{\avgPostElem}[1][{\t[i]}]{\phi(#1)}
\newcommand{\sumDim}{\sum_{i=1}^{\mdim}}
\newcommand{\prodDim}{\prod_{i=1}^{\mdim}}
\newcommand{\seq}[2]{#1_1, #1_2, \ldots, #1_{#2}}
\newcommand{\intSeq}[1]{\left\{ 1, 2, \ldots, #1 \right\}}
\newcommand{\vSeq}[2]{(\seq{#1}{#2})}
\newcommand{\multi}{\frac{\msize!}{\prodDim \x[i]!} \prodDim \t_{i}^{\x[i]}}
\renewcommand{\H}{ \entropy{\X \mid \t}{} }
\newcommand{\omegaElem}{w}
\newcommand{\omegaElemAlt}{w^{(ij)}}
\newcommand{\eqSys}{\W(\t) = \w}
% Clique tree commands
\newcommandx{\msg}[3][1=\delta, 2=i, 3=j]{\mathFix{#1_{#2 \rightarrow #3}}}
\newcommand{\altMsgSym}{\sigma}
\newcommand{\ct}[1]{\mathFix{\mathcal{T}_{#1}}}
\newcommand{\rangeSep}{\set{r}_{i,j}}
\newcommand{\altRangeSep}{\set{r}_{i,j}^{*}}
\newcommandx{\sep}[2][1=i, 2=j]{\mathFix{\set{s}_{#1,#2}}}
\newcommand{\sepVal}{\mathFix{s_{i,j}}}
\newcommandx{\msgMap}[2][1=i, 2=j]{f_{#1,#2}}
\newcommand{\eqScope}{\vartheta}
\newcommand{\ind}{\xi}
\newcommand{\pr}[1]{pr(#1)}
\newcommand{\indVec}[2]{\mathbf{1}_{#1, #2}}
\newcommand{\rankEqSys}{r}
\renewcommand{\M}{\psi}
\newcommand{\mat}{M_{\W}}
\newcommand{\C}[1]{C_{#1}}
\newcommandx{\wPart}[3][1=i, 2=j, 3=\set{w}]{#3_{<(#1,#2)}}
\newcommand{\wSep}{\set{w}^{*}_{i,j}}
\newcommand{\eqScopeSep}[2]{\eqScope_{#1,#2}}
\newcommand{\wSepVal}[2]{w^{*}_{#1, #2}}
\newcommand{\Nb}{Nb_i}

In this section, we examine the derivation of the central probability measure for multinomial models.
Multinomial models play a key role in statistical learning.
By de Finetti’s theorem, any exchangeable sequence of discrete random variables can be represented using a multinomial model.
Exchangeable sequences are fundamental to statistical learning, as they offer a framework for modeling data with
inherent independence and order invariance.

A multinomial model is a parametric model (Definition~\ref{def:param-model}) in which the likelihood function follows a
multinomial distribution.
The configuration of the model is determined by two variables: $\msize$ and $\mdim$.
Each element of the sample space $s \in \set{S}$ can be represent by a $\mdim$ dimensional random vector
\[\X = \vSeq{\x}{\mdim},\] where each \x[i] is a nonnegative integer such that $\sumDim \x[i] = \msize$.
The model parameter is a nonnegative $\mdim$ dimensional real vector \[\t = \vSeq{\theta}{\mdim},\]
where $\sumDim \t[i] = 1$.
The likelihood distributing $\pi(\X \mid \theta)$ is a multinomial distribution
\begin{equation*}
    \pi(\x \mid \t) = \multi \cdot
\end{equation*}

As $\msize$ increases, the posterior distribution of \t converges to the same distribution regardless of the prior.
Therefore, when $\msize$ is sufficiently large, we can use a uniform prior to obtain the posterior potential of the
multinomial parameter.
The uniform prior is conjugate to the multinomial distribution, and the resulting posterior will follow a Dirichlet
distribution:
\begin{align*}
    p(\t \mid \x) &\sim \text{Dir}(\x[1] + 1, \x[2] + 1, \ldots, \x[\mdim] + 1) \\
    &= \prod_{j = 1}^{\mdim - 1} (\msize + j) \multi \cdot
\end{align*}
This implies that for the posterior potential we have
\begin{align*}
    \avgPost[\t] &= \avgPostExpand{\t}{\x} \\
    &= e^{-\H} \prod_{j = 1}^{\mdim - 1} (\msize + j),
\end{align*}
where $\H$ is the entropy of the multinomial distribution with parameter \t.
The entropy of the multinomial distribution can be written in the following form:
\[
    \H =  - \ln(n!) - \sumDim \ln \avgPostElem,
\]
where
\begin{equation}
    \avgPostElem = \exp \left\{ n \t[i] \ln \t[i] -
    \sum_{j = 0}^{n} \ln(j!) \binom{n}{j} \t[i]^{j} (1 - \t[i])^{n - j} \right\} \cdot
    \label{eq:pp_multi_elem}
\end{equation}
Therefore, for the posterior potential of the multinomial parameter we have
\begin{equation}
    \avgPost[\t] = (\msize + \mdim - 1)! \prodDim \avgPostElem \cdot
    \label{eq:pp_multi}
\end{equation}

For the central probability measure of a multinomial model, we usually consider a query set that consists of random
variables corresponding to fusions of the multinomial categories. %todo: should be rewrittten later

Let $\X = \vSeq{\x}{\mdim}$ be a random vector representing an element of the sample space of a multinomial model.
A fusion random variable \Y is obtained by summing up some entries of \X.
More precisely, if $\set{A}_1, \ldots, \set{A}_{\mdim'}$ is a partition of the set $\intSeq{\mdim}$, each value
of \Y is a vector $\vSeq{y}{\mdim'}$ where
\[
    \rval[j]{y} = \sum_{i \in \set{A}_j} \x[i], \qquad j = 1, \ldots, \mdim'\ \cdot
\]
The fusion variable \Y also follows a multinomial distribution with the parameter $\w = \vSeq{\omegaElem}{\mdim'}$,
where
\[
    \omegaElem_j = \sum_{i \in \set{A}_j} \t[i], \qquad j = 1, \ldots, \mdim'\ \cdot
\]
For example $(\t[1] + \t[5], \t[2], \t[4] + \t[7] + \t[8],  \ldots)$ fully parametrizes the fusion variable
$(\x[1] + \x[5], \x[2], \x[4] + \x[7] + \x[8],  \ldots)$.

Suppose that in a multinomial model we aim to find the central probability measure for a query set
$\Qset = \{\X, \seqRv[Y]{k}\}$, where each \Y[i] is a fusion variable, and \X represents the elements of the sample
space.
For using theorem~\ref{th:fixed_point}, we need to obtain $\avgPost$, where \w[i] is the parameter of \Y[i],
and also $\avgPost[\w]$, where $\w = \vSeq{\w}{k}$.
Note that each \w[i] is a multinomial parameter.

Each $\avgPost$ can be easily obtained using Equation~\ref{eq:pp_multi}.
However, calculating $\avgPost[\w]$ requires integration:
\[
    \avgPost[\w] = \int_{\omegaArea} \avgPost[\t] d\t \cdot
\]
This integration is performed over the set of all nonnegative solutions to the linear system of equations $\eqSys$.
Here, \W is a linear map with a matrix $\mat$ consisting solely of $0$ and $1$ entries.
The range of \W typically has much lower dimensionality than \t, and the system of equations contains
many free variables.
This equation system has a solution when \w is inside the convex hull of the columns of $\mat$.

We convert this integration into an inference problem in a probabilistic graphical model, and then use a slightly
modified version of the clique tree message passing~\cite{koller2009probabilistic} algorithm.

For representing equations of the linear system $\eqSys$ by a graphical model, we use indicator factors.
Let $\eqScope \subseteq \{\seq{\t}{\mdim}\}$, and $0 \leq \omegaElem \leq 1$.
An indicator factor $\ind$ is a function with the scope $\{\eqScope, \omegaElem\}$ such that:
\[
    \ind(\eqScope, \omegaElem) = \begin{cases}
                                     1 \quad &  \sum_{\t[i] \in \eqScope} \t[i] = \omegaElem, \\
                                     0 & \text{otherwise} \cdot
    \end{cases}
\]
For example $\ind(\t[2], \t[5], \t[6], \omegaElem)$ is $1$ when $\t[2] + \t[5] + \t[6] = w$, and is $0$ otherwise.

Suppose the rank of $\mat$ is $\rankEqSys$.
We select $\rankEqSys$ linearly independent equations from $\eqSys$, and define an indicator factor for every
equation.
Then, we construct an unnormalized measure $\M$:
\begin{equation}
    \M(\t, \seq{\omegaElem}{\rankEqSys}) =
    \prodDim \avgPostElem \prod_{k = 1}^{\rankEqSys} \ind(\eqScope_k, \omegaElem_k) \cdot
    \label{eq:tree_measure}
\end{equation}

Clearly, marginalizing $\M$ over \t yields $\avgPost[\w]$.
To achieve this, we construct a clique tree for $\M$ that has at least one clique $\C{\omegaElem}$, containing all
$\omegaElem_k$ for $k \in \intSeq{\rankEqSys}$.
By performing message passing and selecting $\C{\omegaElem}$ as the root of the tree, we can compute the desired
marginal: $\M(\omegaElem_1, \ldots, \omegaElem_{\rankEqSys})$.
We denote this clique tree by $\ct{\M}$.

In $\ct{\M}$ each equation and each variable of the equation system $\eqSys$ is associated with a clique.
Let $\C{i}$ and $\C{j}$ be two adjacent cliques in $\ct{\M}$ with the sepset \sep.
Without loss of generality, we assume that the root $\C{\omegaElem}$, is in the $\C{j}$ side of the tree.
Let $\wPart$ be the set of all $\omegaElem_k$ for $k \in \intSeq{r}$,
such that an indicator $\ind(\cdot, \omegaElem_k)$ is associated with a clique in the $\C{i}$ side of the tree.
We can think of $\wPart$ as the set of all equations that are associated with the $\C{i}$ side of the tree.
Let $\eqScopeSep{i}{j}$ be the set of all \t[i] for $i \in \intSeq{\mdim}$ (i.e. the variables of the equation system)
that are in the scope of both $\C{i}$ and $\C{j}$.
Due to the running intersection property, we have \[ \sep = \wPart \cup \eqScopeSep{i}{j} \cdot \]
However, during message passing, we can use a simplified sepset instead.

\begin{definition}
    Let $\ct{}$ be a clique tree.
    Let $\rangeSep$ denote the set of all possible assignments to the sepset \sep.
    A \emph{message reparameterization} for $\ct{}$ is a map (i.e. function) $\msgMap$ defined from $\rangeSep$
    to another set $\altRangeSep$ for every $i, j$, which is message preserving.
    That means, for any $\sepVal, \sepVal' \in \rangeSep$, if $\msgMap(\sepVal) = \msgMap(\sepVal')$
    then $\msg(\sepVal) = \msg(\sepVal')$, where \msg denotes the message from $\C{i}$ to $\C{j}$.

    The reparameterization of \msg, is a function \msg[\altMsgSym] defined on $\altRangeSep$ such that for every
    $\sepVal \in \rangeSep$, we have $\msg(\sepVal) = \msg[\altMsgSym](\msgMap(\sepVal))$.
\end{definition}

\begin{proposition}
    We can replace all messages \msg with their reparameterization \msg[\altMsgSym] without affecting the message passing
    algorithm.
\end{proposition}

\begin{proof}
    During message passing no information regarding specific assignments to \sep is passed between cliques.
    $\C{i}$ simply produces \msg for every possible assignment to \sep.
    Let $\Nb$ be the set of indexes of cliques that are neighbors of $\C{i}$.
    Having the mappings $\msgMap$ and $\msgMap[k][i]$ for every $k \in \Nb$,
    the reparameterized messages \msg[\altMsgSym][k][i] can be used to produce \msg[\altMsgSym].
\end{proof}

Suppose $\omegaElem_k \in \wPart$ and $\ind(\eqScope_k, \omegaElem_k)$ is the indicator factor containing
$\omegaElem_k$.
This indicator represents the equation
\[
    \sum_{\t[i] \in \eqScope_k} \t[i] = \omegaElem_k \cdot
\]
We define a new variable $0 \leq \omegaElemAlt_k \leq 1$ for every \mbox{$\omegaElem_k \in \wPart$} such that
\[
    \omegaElemAlt_k = \omegaElem_k - \sum_{\t[i] \in \eqScope_k \cap \eqScopeSep{i}{j}} \t[i] \cdot
\]
For each sepset \sep, there will be a corresponding set of these new variables.
We denote this set by $\wSep$.
We have a map from assignments to \sep into assignments to $\wSep$, which is message preserving.
If two assignments $\sepVal$, $\sepVal'$ to the sepset variables induce the same assignment to
$\wSep$ variables, that implies the equation system corresponding to the $\C{i}$ part of the tree has
the same solution set for $\sepVal$ and $\sepVal'$.
As a result, we will have $\msg(\sepVal) = \msg(\sepVal')$.

Message computation can be simplified by introducing certain constraints on the structure of $\ct{\M}$.

\begin{definition}[Convolution Clique Tree]
    Let $\ct{\M}$ be a clique tree for the factorized measure of Equation \ref{eq:tree_measure}.
    Let $\pr{i}$, for each clique $\C{i}$, be the index of the parent of $\C{i}$, i.e. the neighbor on the
    path to the root clique $\C{\omegaElem}$.
    We refer to $\ct{\M}$ as a \emph{convolution clique tree} if for every $i$ we have
    \[\C{i} - \sep[i][\pr{i}] = \{\t[i]\} \cdot\]
    That is, in each clique exactly one variable is eliminated.
    We also require that each $\avgPostElem$ factor be associated with the clique that eliminates \t[i].
\end{definition}

Note that indicator factors may be associated with any clique as long as the tree remains
family preserving.

\begin{definition}
    In a convolution clique tree, a clique that is associated with at least one indicator factor is an
    \emph{assignment node}.
    Any clique that is not an assignment node is a \emph{convolution node}.
\end{definition}

To have a more convenient notation, we can express messages as functions of vectors.
Thus, the reparameterized message $\msg[\altMsgSym]$ will be a function of a vector $\wSepVal{i}{j}$, with an entry for
each variable in $\wSep$.
Note that each variable in $\wSep$ corresponds to an equation.
Alternatively, $\wSep$ can be viewed as a set of equations.
We define $\indVec{i}{j}$, for each $i$, $j$, to be an indicator vector indicating those equations of $\wSep$ that
include \t[i].

If $\C{i}$ is a convolution node, the outgoing message from $\C{i}$ to $\C{j}$ can be computed by convolution:
\begin{equation}
    \msg[\altMsgSym](\wSepVal{i}{j}) =
    \int \avgPostElem[t] \prod_{k \in \Nb - \{j\}} \msg[\altMsgSym][k][i](\wSepVal{k}{i} - t \indVec{k}{i}) dt
\end{equation}

On the other hand, when $\C{i}$ is an assignment node, for every value of $\wSepVal{i}{j}$ there is only one acceptable
value for \t[i] and the message can be computed without convolution.
Moreover, certain values of $\wSepVal{i}{j}$ will be invalid.
For every indicator factor, if $\t[i] \notin \eqScope$, the corresponding variable in $\wSep$ to that indicator factor
must be always $0$ in the computed message.
If $\t[i] \in \eqScope$, we assign the corresponding variable in $\wSep$ to $t$, then for $\msg[\altMsgSym]$ we have
\begin{equation}
    \msg[\altMsgSym](\wSepVal{i}{j}) =
    \avgPostElem[t] \prod_{k \in \Nb - \{j\}} \msg[\altMsgSym][k][i](\wSepVal{k}{i} - t \indVec{k}{i}) \cdot
\end{equation}

As we discussed in the previous section, we usually need to compute the
posterior potential of the joint feature $\W(\paramValue) = \vSeq{\w}{m}$, where each \w[i] is a function of the model
parameter \paramValue that fully parametrizes some random variable \X[i] in the model.

For example, $(\t[1] + \t[4], \t[2] + \t[3] + \t[5],  \ldots)$ fully parametrizes $(\x[1] + \x[4], \x[2] + \x[3] + \x[5],  \ldots)$.
When we consider fusion variables, $\W(\t)$ will be a linear map that only includes addition.
The matrix of this mapping will include only $0$ and $1$.

We aim to compute the posterior potential of the joint features \W

is a linear map of the model
parameter that only
includes addition.
We can represent this linear map with a matrix, this matrix will only include 1 and 0
We aim to compute the posterior potential of the joint features \W in a multinomial model.
We can think of $\eqScopeSep{i}{j}$ as the set of all variables of the equation system that are associated with
the $\C{i}$ side of the tree.

We may represent \w with a column vector
\[
    \w = \begin{bmatrix}
             \W[1](\paramValue) \\
             \W[2](\paramValue) \\
             \vdots             \\
             \W[m](\paramValue) \\
    \end{bmatrix} =
    \begin{bmatrix}
        \w[1]  \\
        \w[2]  \\
        \vdots \\
        \w[m]  \\
    \end{bmatrix}
\]


\[
    \avgPost[\t] \propto A e^B \prod_{i=1}^{k} \avgPostElem
\]


\[
    \avgPost[\t] \propto A e^{\entropy{\X \mid \t}{}}
\]

\[
    \entropy{\X \mid \t}{} = B + \sum_{i=1}^{k} \ln \avgPostElem
\]
\[
    B = - \ln(n!)
\]
\[
    \avgPost[\t] \propto \prod_{i=1}^{k} \avgPostElem
\]
