In a parametric model, the maximum of divergence happens for a prior distribution
that is concentrated at a single value of the parameter $\paramValue$.
That means, for a parametric model which allows any high peak prior, instead of maximizing over the set of
all acceptable distributions, we can simply maximize over the parameter space, using the conditional version
of the divergence measure.

\begin{lemma}
    \label{lm:DxP_uppper_bound}
    Assume that \pmodel is a parametric model.
    Let \Xpairs be a query set in \Mt.
    For every $P \in \set{P}$ we have
    \begin{equation*}
        \Dx \leq \maxParam \DxCond
    \end{equation*}
\end{lemma}

\begin{proof}
    \newcommand{\RP}{\sumixe \pi(\xeIt[i]) \ln \frac{R(\xIe[i])}{P(\xIe[i])}}

    Let $R$ and $P$ be two arbitrary probability measures in \Mt.
    For every parameter value \paramValue we have:
    \[
        \DxCond[P] - \DxCond[R] = \RP \cdot
    \]
    Conditional divergence is always positive and we have
    \[
        \RP \leq \DxCond \cdot
    \]
    This inequality holds for any \paramValue.
    Therefore, the maximum of the right-hand side w.r.t. \paramValue is also greater than or equal to the
    maximum of the left-hand side:
    \begin{equation}
        \maxParam \RP \leq \maxParam \DxCond \cdot
        \label{eq:ineq-theorem1}
    \end{equation}
    Trivially, for every \paramValue we have
    \[
        \RP \leq \maxParam \RP \cdot
    \]
    \Mt is a parametric model and $\marginalEq[R]{\xe[i]}$, where $r(\paramValue)$ is
    a prior probability distribution.
    Since this inequality holds for every value of \paramValue and $r(\paramValue) \geq 0$, we can multiply both
    sides by $r(\paramValue)$, and integrate.
    Notice that the right hand side is not a function of $\paramValue$ and it remains unchanged
    because $\int \dt[r] = 1$:
    \[
        \DxExpand[R] \leq \maxParam \RP\cdot
    \]
    Now from Inequality~\ref{eq:ineq-theorem1}, for \emph{any} $P \in \set{P}$ and $R \in \set{P}$, it
    follows that
    \[
        \DxExpand[R] \leq \maxParam \DxCond,
    \]
    which proves the lemma.
\end{proof}

\begin{theorem}
    \label{th:Dx_parametric_form}
    Suppose \pmodel is a parametric model, and let $\Xpairs$ be a query set in \Mt.
    If for every value of $\paramValue$ there is a distribution $R \in \set{P}$ such that
    $R(\rval[]{s}) = \pi(\rval[]{s} \mid \paramValue)$ for every $\rval[]{s} \in \set{S}$,
    then for any $P \in \set{P}$ we have:
    \begin{equation}
        \Dx = \maxParam \DxCond  \cdot
        \label{eq:div_parametric}
    \end{equation}
    \label{th:div_for_parametric}
\end{theorem}

\begin{proof}
    For an arbitrary distribution $P \in \set{P}$, we let
    \[
        \paramValue^* = \arg\maxParam \DxCond \cdot
    \]
    In \Mt there should be a distribution $R \in \set{P}$ that equals $\pi(\rval[]{s} \mid \paramValue^*)$
    for every $\rval[]{s} \in \set{S}$.
    Obviously, $R$ and $\pi(\cdot \mid \paramValue^*)$ define the same distribution for any random variable,
    and we have

    \begin{align*}
        \DxExpand[R] &= \DxCondExpand[][\paramValue^*] \\
        &= \maxParam \DxCond \cdot
    \end{align*}
    On the other hand, clearly
    \[
        \maxQ \DxExpand[Q] \geq \DxExpand[R] \cdot
    \]
    Notice that the left hand side is $\Dx$, and hence
    \[
        \Dx \geq \maxParam \DxCond \cdot
    \]
    This inequality and Lemma~\ref{lm:DxP_uppper_bound} prove the theorem.
\end{proof}
















By Equation~\ref{eq:Cx_by_max}, for the central distribution we have
\begin{align*}
    \central &= \arg\max_{P} \int \left(\KlCond{\seqRval{n}}{}\right) \dt \\
    &= \arg\max_{P} \int \sum_{\seqRval{n}} p(\seqRval{n}, \paramValue) \ln
    \frac{p(\paramValue \mid \seqRval{n})}{p(\paramValue)} d\paramValue \cdot
\end{align*}

That implies, the central distribution for our problem is the same as the distribution we obtain when using the
reference prior~\cite{BERNARDO200517} for our main parameter.


In our dice example, we can let $\Qvar = (\X[k+1], \rv[k+2]{x}, \dots, \rv[n]{x})$, representing all
dice rolls from $k$ to $n$.
We then let \rv{e} be a random vector of the previous dice outcomes $(\seqRv{k})$.

This seems to come from the fact that when we use these priors, in the resulted probability measure the estimate for
the distribution of $\XIE'$ differs from what we intuitively estimate.
This estimate tends to have a much higher entropy.
As a result the optimal strategy for \rv{E'} is mostly ignored because for any value of the evidence it yields a
poor expected utility.

It is reasonable to consider that if we find a probability measure which has a closer estimate to our
intuitive estimate for $\XIE'$ distribution, automatic feature selection will be performed within the Bayesian
framework.
We believe that can be done by using a probability measure that is “safe” for $\XIE'$, in the sense we just described.

Throughout this discussion, we will further investigate this idea and try to formulate a systematic approach to
determine such probability measures.


In our earlier discussion, to assess the safety of a probability measure, we realized that we need to
evaluate the optimal Bayesian strategy in a generic way, independent of the utility function.
We also need to determine how the divergence measures of these variables should be combined.
Definition~\ref{def:e-convergence} already specifies the measure for a single query variable with different evidence
variables.
However, in this case, we have different query variables.
When we have different query variables, the incorrect prediction of each variable can incur a separate loss.
Therefore, we believe in this case addition should be used:
\[
    \sum_i \measure{D}
\]
which equals to
\[
    zhoom zhooom
\]
where x is the random vector and e is ...


Even if we cannot find a distribution that has a small divergence from every distribution, still using the distribution
that minimizes the maximum divergence seems a reasonable choice.


\begin{proposition}
    Let \Qvar be a query variable, and \Eset be an evidence set in \Mt.
    If the conditions of Theorem~\ref{th:div_for_parametric} holds, then for any $P \in \set{P}$ we have:
    \[
        \Dx = \maxParam \DxCond{P}{\Eset} \cdot
    \]
\end{proposition}


\begin{lemma}
    Let $p$, and $q$ be two probability distributions for a random variable $\Theta$.
    If for any $\theta$, and a constant $\lambda$, we have
    \[
        \ln \frac{p(\theta)}{q(\theta)} = \lambda
    \]
    then $\lambda = 0$.
\end{lemma}

\begin{proof}
    Suppose, for the sake of contradiction, that $\lambda > 0$.
    This implies for every $\theta$ we have
    \[
        \frac{p(\theta)}{q(\theta)} > 1 \cdot
    \]
    Since $q(\theta) > 0$, we can conclude that $p(\theta) > q(\theta)$.
    This inequality holds for every $\theta$, and therefore
    \[
        \int \dt[p] > \int \dt[q],
    \]
    which is a contradiction.

    If we assume $\lambda < 0$, similarly we can conclude $\int \dt[p] < \int \dt[q]$, which is a contradiction again.
    Hence, $\lambda$ cannot be positive or negative and we must have $\lambda = 0$.
\end{proof}

\begin{theorem}
    \label{th:lambda}
    Let \Qvar be a query variable, and \Evar be an evidence variable in a parametric model \pmodel.
    Assume that each value of the parameter \paramValue, can be represented as a pair $(\ab)$, and for
    every
    \paramA, \paramB, and \rval{e} we have
    \begin{equation}
        \label{eq:th-lambda-independece}
        p(\bIa, \rval{e}) = p(\bIa) \cdot
    \end{equation}

    If for some probability measure $P \in \set{P}$, the conditional divergence of $P$ is a real valued function
    of \paramA:
    \begin{equation*}
        \DxeCond = \lambda(\paramA),
    \end{equation*}
    then $P$ is the central distribution for $\QvarIE$, and
    \begin{equation*}
        \lambda(\paramA) = \ln \int \phiFunc d\paramB,
    \end{equation*}
    where
    \begin{equation*}
        \phiFunc = \phiExp \cdot
    \end{equation*}

\end{theorem}

\begin{proof}
    \newcommand{\lambdaFunc}{\lambda(\paramA)}
    By Bayes' theorem and Equation~\ref{eq:th-lambda-independece} we have
    \begin{align*}
        \frac{\pi(\xIet)}{P(\xIe)} &= \frac{p(\tIxe)}{p(\bIa, \rval{e})p(\paramA \mid \rval{e})} \\
        &= \frac{p(\tIxe)}{p(\bIa)p(\paramA \mid \rval{e})} \cdot
    \end{align*}
    Now, by simple algebra we can verify that
    \begin{equation*}
        \DxeCond = \ln \frac{\phiFunc}{p(\bIa)}
    \end{equation*}
    We let
    \begin{equation*}
        \rhoFunc = \frac{\phiFunc}{\int \phiFunc d\paramB}
    \end{equation*}
    Therefore,
    \begin{equation*}
        \DxeCond = \lambdaFunc + \ln \frac{\rhoFunc}{p(\bIa)}
    \end{equation*}
    where
    \[
        \lambdaFunc =  \ln \int \phiFunc d\paramB
    \]
\end{proof}

\begin{definition}[Generic Parametric Model]
    We say a parametric model \pmodel is \emph{generic}, if for any arbitrary probability distribution $r$,
    there is a probability measure $R \in \set{P}$, such that for every $\rval[]{s} \in \set{s}$
    \[
        \marginalEq[r]{\rval[]{s}}\cdot
    \]
\end{definition}

\begin{proposition}
    A generic parametric model satisfies the conditions of Theorem~\ref{th:Dx_parametric_form}.
\end{proposition}

\begin{theorem}[Minimax theorem~\cite{Du1995}]
    \label{th:minimax}
    Let $\set{X} \subset \mathbb {R}^{n}$ and $\set{Y} \subset \mathbb {R}^{m}$ be compact convex sets.
    If $f:\set{X}\times \set{Y}\rightarrow \mathbb {R}$ is a continuous function that is concave-convex, i.e.

    \begin{itemize}
        \item $f(\cdot ,y):\set{X}\to \mathbb {R}$ is concave for fixed $y$, and
        \item $f(x,\cdot ):\set{Y}\to \mathbb {R}$ is convex for fixed $x$.
    \end{itemize}
    Then we have that
    \begin{equation}
        \max_{x\in \set{X}}\min_{y\in \set{Y}}f(x, y) = \min_{y\in \set{Y}}\max_{x\in \set{X}}f(x,y)\cdot
        \label{eq:minimax}
    \end{equation}
\end{theorem}


\begin{theorem}
    \label{th:central_by_max}
    Consider a generic parametric model \pmodel, and let \Qvar be a query variable, and \Evar be an evidence
    variable in \Mt.
    Suppose that for every probability measures $Q_1, Q_2 \in \set{P}$, and any real number $0 \leq \alpha \leq 1$,
    there is a $Q^* \in \set{P}$, such that for every $\xe$ we have
    \begin{equation}
        Q^*(\xIe) = \convexCond{\xIe}\cdot
        \label{eq:convex_dist_set}
    \end{equation}

    In this model, the central distribution for $\QvarIE$ can be obtained by:
    \begin{align}
        \centralE &= \arg\maxP \int \DxeCond \dt\\
        &= \arg\maxP \Dminimax,
        \label{eq:Cx_by_max}
    \end{align}
    where $\marginalEq[p]{\rval[]{s}}$, for every $\rval[]{s} \in \set{s}$.
\end{theorem}

\begin{proof}
    \newcommandx{\f}[2][1 = r, 2 = P_{\XIE}]{ f(#1, #2)}
    We prove this theorem using the Minimax theorem.
    For that, we define a functional as follows:
    \begin{equation*}
        \f = \int \DxCondExpand \dt[r],
    \end{equation*}
    where $r(\paramValue)$ is an arbitrary probability distribution, and $P_{\XIE}$ represents different
    distributions of \Qvar given different values of \Evar, induced by a probability measure $P \in \set{P}$.

    Since $r(\paramValue)$ can be any distribution, maximizing with respect to $r$ is similar to maximizing
    with respect to $\paramValue$, and we have
    \[
        \centralE = \arg\minP \max_{r} \f\cdot
    \]

    The domain of $r$ is the set of all probability distributions, which is a compact convex set.
    Moreover, from Equation~\ref{eq:convex_dist_set}, it follows that the domain of $P_{\XIE}$ , which is a function
    of both \Qvar and \Evar, is also a compact convex set.
    Thus, the domain of the functional $\f$ is a compact convex set.

    For a fixed $P_{\XIE}$, $\f[\cdot]$ is a linear function, which is both concave and convex.

    On the other hand, for a fixed $r$, if we let $\marginalEq[r]{\xe}$ we have
    \begin{equation}
        \f[r][\cdot] = c - \sumxe R(\xe) \ln P(\xIe),
        \label{eq:max_for_P}
    \end{equation}
    where $c$ is not a function of $P_{\XIE}$.
    If we calculate the Hessian matrix of $\f[r][\cdot]$, with respect to $P_{\XIE}$, we observe that the matrix is
    diagonal, and each element of the main diagonal is $\frac{R(\xIe)}{P(\xIe)^2}$.
    Thus, the hessian matrix of $\f[r][\cdot]$ is positive semi-definite and $\f[r][\cdot]$ is a convex function.
    Consequently, by Theorem~\ref{th:minimax}
    \begin{equation}
        \minP \max_{r} \f = \max_{r} \minP \f\cdot
        \label{eq:divergence_minmax}
    \end{equation}
    From Equation~\ref{eq:max_for_P} we can see that for an arbitrary fixed $r$ we have
    \[
        \minP \f = \maxP \sumxe R(\xe) \ln P(\xIe)\cdot
    \]

    We know that the Kullback–Leibler divergence, and therefore its expected value, is non-negative:
    \[
        \Ex{R}{\Dcond[R]} \geq 0\cdot
    \]
    By simple algebra we get
    \[
        \sumxe R(\xe) \ln P(\xIe) \leq \sumxe R(\xe) \ln R(\xIe)\cdot
    \]
    Recall that \Mt is a generic parametric model.
    That implies $R \in \set{P}$, and we can reach this upper bound by letting $P = R$:
    \[
        \minP \f = \Dminimax[R]\cdot
    \]
    By Equation~\ref{eq:divergence_minmax}, we conclude
    \[
        \centralE = \arg\max_{R \in \set{P}} \int \DxeCond[R] \dt[r] \cdot \qedhere
    \]
\end{proof}

Theorem~\ref{th:central_by_max} requires that in our model the set of acceptable distribution for $\QvarIE$ be a convex
set.
In most cases, this condition cannot be satisfied.
However, if the distribution that is obtained by Equation~\ref{eq:Cx_by_max} is an acceptable distribution in our model,
the theorem still implies that it is a central distribution in our model.
Note that the set of probability distributions is convex.

\begin{theorem}
    \label{th:lambda}
    Under the assumptions of Theorem~\ref{th:central_by_max}, the central distribution for $\QvarIE$ satisfies:
    \begin{equation}
        \DxeCond[\centralE] = \lambda,
        \label{eq:lambda}
    \end{equation}
    where $\lambda$ is a constant.
\end{theorem}
\begin{proof}
    By Theorem~\ref{th:central_by_max}, the central distribution for $\QvarIE$ maximizes
    \[
        \functional{p(\paramValue)} = \Dminimax,
    \]
    with respect to different choices of the prior distribution $p(\paramValue)$, subject to the
    constraint $\int \dt[p] = 1$.

    Applying the Lagrange multiplier technique, the local maximum of $\functional{}$ is a stationary point of the
    Lagrangian functional:
    \[
        \Lagr[p(\paramValue)] = \Dminimax - \lambda \left( \int \dt - 1 \right)\cdot
    \]
    Let us denote the prior distribution corresponding to the central distribution \centralE by $\cPrior$.
    Let $p(\paramValue) = \cPrior + \epsilon \eta(\paramValue)$ be a variation of $\cPrior$, where $\eta(\paramValue)$ is
    a continuously differentiable function with $\eta(0) = \eta(1) = 0$, and $\epsilon$ is a small constant.

    Since $\cPrior$ is an extremizing function for $\functional{p(\paramValue)}$, the lagrangian
    $\Lagr$ has a stationary point where $\epsilon = 0$, and we have
    \[
        \parDerivAt[\Lagr] = 0\cdot
    \]
    Note that
    \begin{align*}
        \de{p(\paramValue)} &= \eta(\paramValue),\\
        \de{P(\xe)} &= \marginal[\eta]{\xe},\\
        \de{P(\rval{e})} &= \marginal[\eta]{\rval{e}}\cdot
    \end{align*}
    Using the chain rule of calculus, we calculate the partial derivative of $\Lagr$ relative to $\epsilon$:
    \begin{align*}
        \parDeriv\ =\ &\int \left( \Dparam  \right) \dt[\eta] \\
        &- \int \left( \sumxe \pi(\xeIt) \frac{\marginal[\eta]{\xe}}{P(\xe)} \right) \dt \\
        &+ \int \left( \sum_{\rval{e}} \pi(\eIt) \frac{\marginal[\eta]{\rval{e}}}{P(\rval{e})} \right) \dt \\
        &- \int \lambda \dt[\eta]
    \end{align*}
    Since $\marginalEq{\xe}$ and $\marginalEq{\rval{e}}$, we get
    \begin{equation*}
        \parDeriv = \int \left(-\lambda + \Dparam \right) \dt[\eta]\cdot
    \end{equation*}
    We let $ \parDerivAt = 0$.
    Since $\eta(\paramValue)$ is an arbitrary function, by applying the fundamental lemma of the calculus of
    variations and letting $\epsilon = 0$, for every value of $\paramValue$ we have
    \[
        \Dparam[\centralE] = \lambda\cdot \qedhere
    \]
\end{proof}

Consider a scenario where we are trying to predict the outcome of a four-sided dice. This dice is unfair, with each
face marked by a binary number: $00$, $01$, $10$, and $11$.
Before making our prediction, we can roll the dice for several times and use the results to learn the associated
probabilities.
We assume that the dice rolls are independent.

Let's focus on determining the central distribution for this problem.
The first step in this process is to establish our query set $\Xpairs$.

In a prediction problem, we are interested in the distribution of the random variable we want to predict,
conditioned on the observed data.
For example, if we roll the dice for three times before making our prediction,
we will need $P(\rv[4]{x} \mid \rv[1]{x},\rv[2]{x},\rv[3]{x})$, where \Qvar denotes the outcome
of the $i$-th dice roll.

Imagine playing a game of chance involving our four-sided dice.
After rolling the dice, we input the outcome into a mysterious machine.
The machine then announces whether we have won or lost the game.
We have no clue how the machine works. We are not even sure if the dice outcome truly affects the machine’s output.
All we know is that the machine is memory-less, and the result of each game is independent.

Our goal is to learn how the machine operates through experimentation.
We aim to be able to predict whether we will win the game after observing the dice outcome.

We assume that, first, we roll the dice $n$ times, and record each outcome.
Next, we input some of these dice outcomes into the machine and observe the result of each game.
As we will see, this assumption is important for deriving the central distribution more easily.

Let us define a query set for this problem.
We denote this set as $\Xpairs$, where each \Qvar is the result of the $i$-th game, and the evidence \rv{e} is a
vector
\[
    (\seqRv{i-1}, \seqRv[y]{n}),
\]
where each \rv{y} denotes the $i$-th dice outcome.

The conditional divergence for \set{x} can be obtained by
\begin{align*}
    \DxeCond &= \KlCond{\rval[1]{x}}{\seqRval[y]{n}} \\
    &+ \KlCond{\rval[2]{x}}{\rval[1]{x},\seqRval[y]{n}} \\
    &+ \KlCond{\rval[3]{x}}{x1, x2, \seqRval[y]{n}} \\
    &+ \ \cdots \\
\end{align*}
After using the chain rule for conditional probability the right hand side simplifies to
\begin{align*}
    \KlCond{\seqRval{n}}{\seqRval[y]{n}} \cdot
\end{align*}

Consequently, an alternative way for defining our query set is to define it as a single
pair $\left\{(\rvec{x}, \rvec{e})\right\}$, where \rvec{x} is the vector of $n$ game's result, and \rvec{e} is the vector of $n$
dice outcome.

Using the new definition for \set{x}, by Equation~\ref{eq:lambda} we have:
\begin{equation*}
    \KlCond[\central]{\vval{x}}{\vval{e}} = \lambda
\end{equation*}
\emph{derive a $\paramValue = (\paramA, \paramB)$ closed form for central dist...}

\[
    \frac{\pi(\vval{x} \mid \vval{e}, \paramValue)}{\central(\vval{x} \mid \vval{e})}
    = \frac{\pi(\paramValue \mid \vval{x}, \vval{e})}{\central(\paramValue \mid \vval{e})}
\]

sdfd

\[
    \KLabVec
\]

Assume that we decide to simplify our learning task.
We choose to consider only the least significant digit of the dice outcome and ignore the other digit.
For example, if the dice outcome is $10$, we treat it as $0$.
This approach decreases the number of possible outcomes of the dice, making the learning process simpler.
However, it also reduces our ability to predict the game’s result accurately.

In order to find a central distribution for this version of our game, we should slightly modify the definition of the
query set.
While each \Qvar remains unchanged, we need to represent each \rv{e} as a vector
\[
    (\seqRv{i-1}, \seqRv[y']{n}),
\]
where each \rv{y'} represents the least significant digit of the dice outcome.
We denote this new query set as \set{x'} and the previous query set as \set{x}.

Following similar steps as we did for \set{x}, we can show that \set{x'} also has a more compact counterpart,
which includes a single pair $(\rvec{x}, \rvec{e'})$, where \rvec{x} is the vector $(\seqRv{n})$, and \rvec{e'} is
the vector
$(\seqRv[y']{n})$.

\emph{explain how the central distribution for this version is different...}

When we have a lot of learning data, there is no point in using this simpler version of our learning task.
However, when the available data is not enough for the more complex version, the simpler version can still produce
relatively meaningful results,
while the data is too small for the more complex version.

Is it possible to have a probabilistic inference framework that is able to automatically choose between these two
versions of the problem based on the quality and amount of available data?
It seems that the central distributing has this ability.
For that, we need to use the central distribution for the query set $\set{x} \cup \set{x'}$.
This seems reasonable, since when we want our probabilistic inference framework to choose between two versions of
our problem, our query set should include random variables of both versions.

\begin{theorem}
    Let \pmodel be a generic parametric model, and $\Xsingles$ be a set of random variables in \Mt.
    Let $\paramFunc$, for every $i$, be a function of the parameter $\param$ that fully parametrizes \Qvar,
    so that for $\paramFuncValue = \paramFunc(\paramValue)$ we have:
    \begin{equation}
        \pi(\xIt) = \pi \left( \rval{x} \mid \paramFuncValue \right)\cdot
        \label{eq:func_of_theta}
    \end{equation}
    The prior distribution corresponding to the central distribution for \set{X} in \Mt can be characterized
    by the following fixed point equation:
    \begin{equation}
        \cPrior \propto \left( \prod_i \cMass{\tIw} \rhoPrior \right)^{\frac{1}{|\set{x}|}},
        \label{eq:fixed_point_cx}
    \end{equation}
    where
    \[
        \rhoPrior \propto \exp \left\{\sum_{\rval{x}} \pi(\xIw) \ln \cMass{\wIx} \right\}\cdot
    \]

\end{theorem}

\begin{proof}
    First, we show that the set of distributions of each \Qvar is a convex set.
    Let $Q^*(\rval{x}) = \convexCond{\rval{x}}$, for some $Q_1, Q_2 \in \set{P}$, $0 \leq \alpha \leq 1$ and
    arbitrary $i, \rval{x}$.

    \Mt is a parametric model.
    Therefore,
    \begin{align*}
        Q^*(\rval{x}) &= \alpha \marginal[q_1]{\rval{x}} + (1 - \alpha) \marginal[q_2]{\rval{x}}\\
        &= \int \pi(\xIt) (\convexCond[q]{\paramValue}) d\paramValue\cdot
    \end{align*}
    $\convexCond[q]{\paramValue}$ is a valid prior distribution and \Mt is a generic parametric model.
    That implies $Q^* \in \set{P}$.

    Thus, by Theorem~\ref{th:lambda} the central distribution of \set{X} satisfies
    \begin{equation}
        \sumOverix \pi(\xIt) \ln \frac{\pi(\xIt)}{\central(\rval{x})} = \lambda\cdot
        \label{eq:lambda_th_proof}
    \end{equation}
    Moreover, from Equation~\ref{eq:func_of_theta} and Bayes' theorem it follows
    \begin{align*}
        \sumOverix \pi(\xIt) \ln \frac{\pi(\xIt)}{\central(\rval{x})}
        &= \sumOverix \pi(\xIw) \ln \frac{\pi(\xIw)}{\central(\rval{x})}\\
        &= \sumOverix \pi(\xIw) \ln \frac{\cMass{\wIx}}{\cPrior[(\paramFuncValue)]}\\
        &= \sum_i \ln \frac{\rhoPrior}{\cPrior[(\paramFuncValue])}\cdot
    \end{align*}
    Since each $\paramFunc$ is a function of $\param$, for $\paramFunc(\paramValue) = \paramFuncValue$
    we have $\cMass{\paramValue, \paramFuncValue}=\cPrior$.
    Therefore,
    \begin{equation*}
        \cPrior[(\paramFuncValue)] = \frac{\cPrior}{\cMass{\tIw}}\cdot
    \end{equation*}
    Now we rewrite Equation~\ref{eq:lambda_th_proof}:
    \begin{align*}
        |\set{X}| \ln \cPrior &= \sum_i \ln \left(\cMass{\tIw} \rhoPrior \right) - \lambda\\
        \cPrior &= \left( e^{-\lambda} \prod_i \cMass{\tIw} \rhoPrior \right)^{\frac{1}{|\set{x}|}} \qedhere
    \end{align*}
\end{proof}


\begin{theorem}
    Let \pmodel be a generic parametric model, and $\Xpairs$ be a set of random variables in \Mt.
    Let $\paramFunc$, for every $i$, be a function of the parameter $\param$ that fully parametrizes \Qvar,
    so that for $\paramFuncValue = \paramFunc(\paramValue)$ we have:
    \begin{equation}
        \pi(\xIt) = \pi \left( \rval{x} \mid \paramFuncValue \right)\cdot
        \label{eq:func_of_theta}
    \end{equation}
    The prior distribution corresponding to the central distribution for \set{X} in \Mt can be characterized
    by the following fixed point equation:
    \begin{equation}
        \bIaRoot \propto \left( \prod_i \frac{\abIab \rhoPrior}{\aIa} \right)^{\frac{1}{|\set{x}|}},
        \label{eq:fixed_point_cx}
    \end{equation}
    where
    \[
        \rhoPrior \propto \exp \left\{ \sumxe \xeIba \ln \bIxe \right\} \cdot
    \]

\end{theorem}

\begin{proof}
    First, we show that the set of distributions of each \Qvar is a convex set.
    Let $Q^*(\xIe) = \convexCond{\xIe}$, for some $Q_1, Q_2 \in \set{P}$, $0 \leq \alpha \leq 1$ and
    arbitrary $i, \xe$.

    \Mt is a parametric model.
    Therefore,
    \begin{align*}
        Q^*(\xIe) &= \alpha \int \xIebFull q_1(\beta \mid \rval {e}) d\beta + (1 - \alpha) \marginal[q_2]{\rval{x}}\\
        &= \int \pi(\xIt) (\convexCond[q]{\paramValue}) d\paramValue\cdot
    \end{align*}
    $\convexCond[q]{\paramValue}$ is a valid prior distribution and \Mt is a generic parametric model.
    That implies $Q^* \in \set{P}$.

    Thus, by Theorem~\ref{th:lambda} the central distribution of \set{X} satisfies
    \begin{equation}
        \Dparam[\central] = \lambda\cdot
        \label{eq:lambda_th_proof}
    \end{equation}
    Moreover, from Equation~\ref{eq:func_of_theta} and Bayes' theorem it follows
    \begin{align*}
        \lambda
        &= \Dparam[\central]\\
        &= \sumxe \xeIba \ln \frac{\xIeb}{\central(\xIe)} \\
        &= \sumxe \xeIba \ln \frac{\bIxe}{\cMass(\paramB \mid \rval{e})} \\
        &= \sum_i \ln \frac{\rhoPrior}{\bIa}\cdot
    \end{align*}
    Since each $\paramFunc$ is a function of $\param$, for $\paramFunc(\paramValue) = \paramFuncValue$
    we have $\cMass{\paramValue, \paramA, \paramB}=\cPrior$ $\cMass{\alpha , \paramA} = \cMass{\alpha}$.
    Therefore,
    \begin{equation*}
        \bIa = \frac{\aIa}{\abIab} \bIaRoot \cdot
    \end{equation*}
    Now we rewrite Equation~\ref{eq:lambda_th_proof}:
    \[
        |\set{X}| \ln \bIaRoot = -\lambda + \sum_i \ln \frac{\abIab \rhoPrior}{\aIa}
    \]
    Then:
    \begin{align*}
        \bIaRoot
        &= \left( e^{-\lambda} \prod_i \frac{\abIab \rhoPrior}{\aIa} \right)^{\frac{1}{|\set{x}|}} \\
        &= \left( e^{-\lambda} \prod_i \frac{\bIaRoot \rhoPrior}{\bIa} \right)^{\frac{1}{|\set{x}|}} \\
        &= \bIaRoot \left( \prod_i \frac{ \rhoPrior}{\bIa} \right)^{\frac{1}{|\set{x}|}} \\
        &= \bIaRoot \left(e^{-\lambda} \prod_i
        \frac{\rhoPrior[(\paramA, \paramB) \cMass(\paramA)]}{\cMass(\paramA, \paramB) \rhoPrior[(\paramA)] } \right)
        ^{\frac{1
        }{|\set{x}|}}
        \qedhere
    \end{align*}
\end{proof}






Let’s revisit our discussion from the previous section.
We saw that in Bayesian framework when we have evidence \rv{e'}, such that $\rv{e'} = f(\rv{e})$, the
optimal strategy for \rv{e} always has a greater expected utility than any strategy that uses \rv{e'}.
We stated that we believe...


\begin{definition}[Aggregator]
    Consider two probabilistic models \model and \aggmodel.
    Let \Qvar be a query variable and $\Eset = \{\seqRvInf[e]\}$ be an evidence set in \M.
    Also, let \agg{\rv{e}}, \agg{\Qvar}, and \rv{i} be random variables defined on \agg{\set{s}} in \Magg.
    We refer to \agg{\rv{x}}, \agg{\rv{e}} as the \emph{aggregated} query and evidence variables, and \rv{i} as the
    \emph{selector} variable.

    Suppose that for a probability measure $P \in \set{P}$ there exists a probability measure
    $\agg{P} \in \agg{\set{P}}$, such that for any index \rval{i}, and every values \QvarVal, and \rval[i]{e}
    there is some \agg{\QvarVal}, and \agg{\rval{e}}, where we have
    \begin{equation}
        P(\Qvar = \QvarVal, \rv[i]{e} = \rval[i]{e}) =
        \agg{P}(\agg{\Qvar} = \agg{\QvarVal}, \assign{\agg{e}} \mid \assign{I}) \cdot
        \label{eq:th1-1}
    \end{equation}
    Furthermore, \agg{\Qvar} and \rv{I} are conditionally independent given \agg{\rv{E}}:
    \begin{equation}
        \agg{P}(\aggXIE, \rv{I}) = \agg{P}(\aggXIE) \cdot
        \label{eq:th1-2}
    \end{equation}
    We call \agg{P} an \emph{aggregator of $P$ with respect to $\QvarIEset$}.
\end{definition}

\begin{proposition}
    By Equations~\ref{eq:th1-1} and~\ref{eq:th1-2} we have
    \begin{equation*}
        P(\QvarVal \mid \rval[i]{e}) = \agg{P}(\aggxIe) \cdot
    \end{equation*}
\end{proposition}

\begin{definition}[Aggregate Model]
    \label{def:aggregate-model}
    Consider a probabilistic model \model.
    Let \Qvar be a query variable, and \Eset be an evidence set in \M.
    We say a model \aggmodel is the \emph{aggregate model} of \M with respect to $\QvarIEset$,
    If every probability measure in \Magg is the aggregator of a probability measure in \M with respect to $\QvarIEset$.
    %, and every probability measure in \M has at least one aggregator in \Magg with respect to $\QvarIEset$.
\end{definition}

\begin{definition}[Selective Aggregate Model]
    Let \Qvar be a query variable, and \Eset be an evidence set in \model.
    Let \Magg be an aggregate model of \M with respect to $\QvarIEset$.
    We say \Magg is \emph{selective}, if for every $P \in \set{P}$ and any value \rval{i} of the selector
    variable \rv{I}, there is an aggregator of $P$ in \Magg, such that $\agg{P}(i) = 1$.

\end{definition}


\begin{theorem}
    Let \Qvar be a query variable, and \Eset be an evidence set in a probabilistic model \model.
    Suppose that \aggmodel is a selective aggregate model of \M with respect to $\QvarIEset$.
    Let \agg{\rv{x}}, \agg{\rv{e}} be the aggregated query and evidence variables in \Magg.
    If $\agg{P} \in \agg{\set{P}}$ is an aggregator of the probability measure $P \in \set{P}$
    with respect to $\QvarIEset$, then we have
    \begin{equation*}
        \Dx = \aggDxP \cdot
    \end{equation*}

    In addition, the central distribution for $\agg{\Qvar}|\agg{\rv{e}}$ is an aggregator of the central
    distribution for $\QvarIEset$.
\end{theorem}

\begin{proof}
    \newcommand{\aggExpKL}[1]{\ExpKL[\agg{\rval{x}}][\agg{\rval{e}}][\agg{#1}][\agg{P}]}
    Suppose $\agg{P} \in \agg{\set{P}}$ is an aggregator of the probability measure $P \in \set{P}$
    with respect to $\QvarIEset$.
    Let
    \begin{equation*}
        \agg{R} = \arg\max_{\agg{Q} \in \agg{\set{P}}} \aggExpKL{Q}.
    \end{equation*}
    Since \Magg is an aggregate model, $\agg{R}$ must be an aggregator of some probability measure $R \in \set{P}$.
    It follows that
    \begin{align*}
        \aggDxP
        &= \aggExpKL{R} \\
        &= \sum_i \agg{R}(\rval{i}) \ExpKL[][{\rval[i]{e}}][R] \\
        &\leq \max_i \ExpKL[][{\rval[i]{e}}][R] \cdot
    \end{align*}
    This implies
    \begin{equation}
        \aggDxP \leq \Dx \cdot
        \label{eq:th-2-proof-1}
    \end{equation}

    Similarly, let
    \begin{equation*}
    (S,k)
        = \arg\max_{(Q,i)} \ExpKL[][{\rval[i]{e}}] \cdot
    \end{equation*}
    \Magg is a selective aggregate model.
    This means that $S$ must have an aggregator \agg{S} in \Magg, which selects $k$ by assigning it a
    probability of 1: $\agg{S}(k) = 1$.
    Therefore,
    \begin{align*}
        \Dx
        &= \ExpKL[][{\rval[k]{e}}][S] \\
        &= \sum_{\aggxe} \agg{S}(\aggxe \mid k) \ln\frac{\agg{S}(\aggxIe)}{\agg{P}(\aggxIe)} \\
        &= \aggExpKL{S} \\
        &\leq \aggDxP \cdot
    \end{align*}
    From this and Inequality~\ref{eq:th-2-proof-1}, we conclude that
    \begin{equation*}
        \Dx = \aggDxP \cdot
    \end{equation*}

    To prove the second part of the theorem, let \agg{C} be a central distribution
    for $\agg{\Qvar}|\agg{\rv{e}}$.
    Since \Magg is an aggregate model for \M, \agg{C} must be an aggregator for some probability
    measure $C \in \agg{\set{P}}$.
    If we assume, by contradiction, that $C$ is not a central distribution for $\QvarIEset$ in \M, then there must
    be a probability
    measure $R \in \set{P}$ such that:
    \begin{equation*}
        \Dx[R] < \Dx[C] = \aggDxP[C] \cdot
    \end{equation*}
    On the other hand, since \Magg is a selective model, $R$ must have an aggregator $\agg{R} \in \agg{\set{P}}$,
    and since \agg{C} is a central distribution in \Magg, we have
    \begin{equation*}
        \Dx[R] = \aggDxP[R] \geq \aggDxP[C],
    \end{equation*}
    which is a contradiction.
\end{proof}

