When we lack prior knowledge of an environment, it is still not difficult to identify some distributions that are
not suitable choices for \prior.
For instance, any distribution that assigns zero probability to certain values of \paramValue is not a good choice.
If we use such a prior, evidence can never convince us that the value of \paramValue lies within those
excluded values.

We should note that, in this context, we cannot objectively assert that there is some type of
underlying process in the environment for generating different values of \paramValue that does not consider zero
probability for any value of \paramValue.
Our argument is subjective.
We consider some priors to be unsafe because they have some characteristics that appear to be problematic:
in the obtained posterior, some values of the parameter are excluded regardless of the evidence.

We can generalize this idea and use a similar subjective approach to determine a somewhat “safe”
prior distribution.
Recall that our probabilistic model for the environment consists of a set of acceptable probability measures \set{P}.
Suppose that we choose a probability measure $C \in \set{P}$, and determine the optimal Bayesian strategy in $C$.
If the expected loss of this strategy in any other probability measure
$P \in \set{P}$ is close to the optimal strategy, we can say that using $C$ is safe, in the
sense that the optimal strategy obtained using $C$, is a near optimal strategy in any other acceptable probability
measure in our model.


The probability measure that we choose represents our beliefs about the environment.
It can be argued that this choice must depend solely on the environment.
As long as the environment is the same, we should not change our choice.
For example, if our loss function changes, or if the evidence that we get from the environment becomes more or
less informative, none of these can change our beliefs about the environment and therefore our chosen
probability measure.
We will use this principle several times in this discussion and refer to it as the \emph{principle of objectivity}.

Unfortunately, the expected loss of a strategy is a functional of the loss function.
Therefore, we cannot directly use the expected loss of the optimal Bayesian strategy for evaluating
different probability measures.
We need a measure that quantifies the similarity between two probability measures while it ignores the
specific loss function we are using.

Suppose that for an environment, we have decided on a probabilistic model \M, and without any particular prior
knowledge, we have chosen a probability measure $P$ from our model.
In particular, we are interested in the distribution of a random variable \X.

We ask an expert---a person familiar with the environment---to evaluate our probability measure $P$.
Presumably, that expert has his own beliefs about the environment.
Therefore, he believes, instead of $P$, we should use a different probability measure $Q$.
When evaluating $P$, he would try to measure the loss of using the incorrect distribution $P(\X)$,
while he believes the correct distribution is $Q(\X)$.

Let's assume that a real number can be used to measure this loss, and denote it as $\D[\X]$.
It seems reasonable, as $P$ gets closer to $Q$ this measure decreases, and increases when $P$ diverges from $Q$.
Therefore, $\D$ effectively is a measure of the divergence of $P(\X)$ from $Q(\X)$, when $Q$ is
the believed true probability measure.

Interestingly, if we make certain assumptions about the properties of this divergence measure,
it turns out that---up to a constant factor---it must be equal to the Kullback–Leibler (KL) divergence.

Alternatively, by adopting a more minimal set of properties, we can prove that if we accept Shannon’s entropy as a
measure of the uncertainty of a distribution, we should also consider KL divergence as the appropriate method for
measuring divergence between distributions.

\begin{theorem}
    Let \X be a discrete random variable.
    Suppose that $\D[\X]$ is a divergence measure that quantifies the divergence of $P(\X)$ from $Q(\X)$.
    Consider the following properties:
    \begin{description}
        \item[Consistency with entropy] Let $\varOmega$ be a continuous random variable. If $U(\varOmega)$ is the
        uniform distribution
        with the same support as $Q(\varOmega)$, then we have
        \[
            \D[\varOmega][Q][U] = \entropy{U}{\varOmega} - \entropy{Q}{\varOmega},
        \]
        where $\entropy{}{}$ denotes Shannon's entropy.
        \item[Additivity] For any two discrete random variables $\XY$
        \[
            \D[\XY] = \D + \sumx \D[\YIx]Q(\rval[]{x})\cdot
        \]
    \end{description}
    If \measure{D} satisfies these properties, then it is the Kullback-Leibler divergence.
\end{theorem}

\begin{proof}
    \newcommand{\T}{\varOmega}
    \renewcommand{\t}{\omega}
    \newcommand{\tIx}{\t \mid \rval[]{x}}
    \newcommand{\TIx}{\T \mid \rval[]{x}}
    \newcommand{\TX}{\T, \X}
    \newcommand{\tx}{\t, \rval[]{x}}
    \newcommand{\tent}[1]{\int q(#1) \ln q(#1) d\t}

    \newcommand{\Qx}{Q(\rval[]{x})}
    Let $P(\X)$ and $Q(\X)$ be two arbitrary distributions for a discrete random variable \X.
    We define a new continuous random variable $\T$ and let
    \begin{equation*}
        p(\T = \t \mid \rvEq) =
        \begin{cases}
            \frac{1}{P(\rval[]{x})} & 0 \leq \t \leq P(\rvEq),\\
            0 & \text{otherwise}\cdot
        \end{cases}
    \end{equation*}
    Notice that both $P(\T \mid \X)$ and $P(\TX)$ are uniform distributions, and
    $\entropy{P}{\TIx} = \ln P(\rval[]{x})$, $\entropy{P}{\TX} = 0$.

    We define $Q(\TIx)$ to be an arbitrary distribution that has the same support as $P(\TIx)$.
    This ensures that $Q(\TX)$ and $P(\TX)$ have the same support as well.
    Thus, we have
    \begin{align*}
        \D[\TX] &= \entropy{P}{\TX} - \entropy{Q}{\TX}\\
        &= \sumx \tent{\tx}\\
        &= \sumx \Qx \int q(\tIx) \ln q(\tx) d\t,
    \end{align*}
    and
    \begin{align*}
        \D[\TIx] &= \entropy{P}{\TIx} - \entropy{Q}{\TIx}\\
        &= \ln P(\rval[]{x}) + \tent{\tIx}\cdot
    \end{align*}
    Now, we use the additivity property to obtain a formula for our divergence measure:
    \begin{align*}
        \D &= \D[\TX] - \sumx \D[\TIx]\Qx \\
        &= \sumx \Qx  \left( \int q(\tIx) \ln \frac{q(\tx)}{q(\tIx)}d\t - \ln P(\rval[]{x}) \right)\\
        &= \sumx \Qx  \left( \ln \Qx \int q(\tIx) d\t - \ln P(\rval[]{x}) \right)\\
        &= \sumx \Qx \ln \frac{\Qx}{P(\rval[]{x})}\cdot \qedhere
    \end{align*}
\end{proof}

In this theorem, the first property simply states that the entropy of a distribution should be related to the
divergence of the uniform distribution from it.
The more the divergence is, the less the entropy must be.

The second property tells us that the divergence is an additive quantity.
We know that the divergence of $P(\XY)$ from $Q(\XY)$ is a measure of the generic loss of using $P(\XY)$
when we believe $Q(\XY)$ is the true distribution.
To calculate this loss, we can assume that \X happens before \Y.
In that way, this loss would include the loss of using $P(\X)$, and then, if we observe
$\assign{X}$, which can happen with probability $Q(\rval[]{x})$, it would also include the loss of
using $P(\Y \mid \assign{x})$.
This property indicates that for combining these individual terms we should use addition.

Thus, if $Q$ is the probability measure that represents our beliefs, we can use $\D$ to evaluate any other
probability measure $P$, with respect to a random variable \X.
In other words, we can say that we are evaluating $P(\X)$.

When we have two different random variables \X and \Y, there will be two distinct cases that should not be
confused:
We may want to evaluate $P(\XY)$, or may want to evaluate $P(\X)$ and $P(\Y)$.
Evaluating the joint distribution $P(\XY)$ is straightforward and can be done by defining a new random variable
$\rv{Z} = (\XY)$.
However, the second case may present more challenges.
Evaluating the marginal distributions $P(\X)$ and $P(\Y)$ separately is the same as evaluating $P(\XY)$ when \X
and \Y are independent.
Here, we can use a similar argument to what we used for the additive property:
We want to evaluate the loss of $P(\XY)$, If \X happens first we will face the loss of $P(\X)$,
then when \Y happens we will face the loss of $P(\Y)$ because \X and \Y are independent.
Therefore we should use addition:
\[
    \D[\X] + \D[\Y].
\]

We may use the KL divergence to measure the agreement of a model about a specific distribution:

\begin{definition}[$\epsilon$-convergence]
    \label{def:e-convergence}
    In a probabilistic model \model, let \X and \E be discrete random variables.
    We say $\XIE$ (\X conditioned on \E) \emph{\econverges by $P \in \set{p}$},
    if for any probability measure $Q \in \set{p}$ we have:
    \begin{equation*}
        \Ex{Q}{\D[\XIe]} < \epsilon,
    \end{equation*}
    where $\Ex{Q}{\,\cdot\,}$ denotes expectation relative to $Q$ and $\D[\XIe]$ is the Kullback-Leibler divergence
    of $P(\XIe)$ from $Q(\XIe)$:
    \[
        \D[\XIe] = \sum_{\rval{x}} Q(\xIe) \ln \frac{Q(\xIe)}{P(\xIe)}\cdot
    \]
\end{definition}

$\epsilon$-convergence is closely related to the concept of Bayesian convergence, where the posterior converges to
the same distribution regardless of the prior distribution.

As an example, consider a scenario where we are trying to predict the outcome of a four-sided dice. This dice is
unfair, with each face marked by a binary number: $00$, $01$, $10$, and $11$.
Before making our prediction, we can roll the dice multiple times, assuming that each roll is independent.

If we let \rv{e} be a vector representing the first 10 dice rolls and \rv{x} be the outcome of the next roll,
\XIE \econverges by $P_u$ for $\epsilon \geq 0.109$, where $P_u$ is the probability measure obtained from
assuming a uniform prior for the multinomial parameters.
If \rv{e} represents the first 20 outcomes, then we can choose any $\epsilon \geq 0.073$.

In our example, the chosen prior for the multinomial parameters affects the value of $\epsilon$.
In other words, different probability measures in our model have different convergence properties.
If there is a probability measure that provides $\epsilon$-convergence for a very small $\epsilon$, we can hardly
justify using any other probability measure.

However, that probability measure may not always exist.
Moreover, we are unsure of what value of $\epsilon$ would be sufficiently small.
This becomes more problematic when we need to consider more than one distribution.
For example, suppose that we are interested in the distributions of both $\rv{X}|\rv[1]{E}$ and $\rv{X}|\rv[2]{E}$ .
As we discussed earlier, when dealing with multiple distributions we should consider the sum of their KL divergences.
Unfortunately, that would make determining the appropriate value of $\epsilon$ even harder.

\begin{definition}[Query Set]
    A \emph{query set} is a set of pairs of discrete random variables, all defined on the same sample space.
\end{definition}

\begin{definition}
    Let \Xpairs, be a query set in a probabilistic model \model.
    We define the \emph{divergence measure of $P \in \set{P}$ for \Qset} as follows:
    \begin{align}
        \label{eq:div-def}
        \Dx &= \max_{Q \in \set{P}} \DxExpand, \\
        &= \maxQ \sumixe Q(\assign[i]{x} , \assign[i]{e}) \ln
        \frac{Q(\assign[i]{x} \mid \assign[i]{e})}{P(\assign[i]{x} \mid \assign[i]{e})} \cdot
        \label{eq:div_measure}
    \end{align}
\end{definition}

Note that we usually simplify our notation and instead of writing the full assignment to a random variable, we only
write the assigned value.
For example, instead of $Q(\assign[i]{x} , \assign[i]{e})$ we write: $Q(\xe[i])$.

\begin{proposition}
    \XIE \econverges by $P$, if and only if the divergence measure of $P$ for $\Qset = \{(\XE)\}$ is
    less than $\epsilon$.
\end{proposition}

We can avoid all these hurdles by simpling choosing the probability measure that has the smallest divergence measure.
Subjectively, this probability measure is the safest choice in our model and it turns out that it behaves well even
when the divergence measure is not very small.

\begin{definition}[Central Probability Measure]
    In a model \model, we define the \emph{central probability measure} for a query set \Qset, to be a probability
    measure $\central \in \set{P}$ which minimizes the divergence measure for \Qset:
    \begin{equation*}
        \central = \arg\minP \Dx\cdot
        \label{eq:center}
    \end{equation*}
\end{definition}

When we need to choose one of the probability measures of our model, the central probability measure for a query set
appears to be a reasonable and safe choice.
However, if our query set depends on our specific experimental setup, we are violating the principle of objectivity.
To avoid this, one natural solution is to let the query set include all conditional forms that are relevant.

In our dice example, we can let $\Qvar = (\X[k+1], \rv[k+2]{x}, \dots, \rv[n]{x})$, representing all
dice rolls from $k$ to $n$.
We then let \rv{e} be a random vector of the previous dice outcomes $(\seqRv{k})$.
Here, the choice of $k$ and $n$ is based on our assumptions about the complexity of the problem: Only after seeing at
least $k$ outcomes, convergence is meaningful and after $n$ outcomes it becomes trivial.

This seems to come from the fact that when we use these priors, in the resulted probability measure the estimate for
the distribution of $\XIE'$ differs from what we intuitively estimate.
This estimate tends to have a much higher entropy.
As a result the optimal strategy for \rv{E'} is mostly ignored because for any value of the evidence it yields a
poor expected utility.

It is reasonable to consider that if we find a probability measure which has a closer estimate to our
intuitive estimate for $\XIE'$ distribution, automatic feature selection will be performed within the Bayesian
framework.
We believe that can be done by using a probability measure that is “safe” for $\XIE'$, in the sense we just described.

Throughout this discussion, we will further investigate this idea and try to formulate a systematic approach to
determine such probability measures.


In our earlier discussion, to assess the safety of a probability measure, we realized that we need to
evaluate the optimal Bayesian strategy in a generic way, independent of the utility function.
We also need to determine how the divergence measures of these variables should be combined.
Definition~\ref{def:e-convergence} already specifies the measure for a single query variable with different evidence
variables.
However, in this case, we have different query variables.
When we have different query variables, the incorrect prediction of each variable can incur a separate loss.
Therefore, we believe in this case addition should be used:
\[
    \sum_i \measure{D}
\]
which equals to
\[
    zhoom zhooom
\]
where x is the random vector and e is ...


In this definition, the query set $\Xpairs$ plays a crucial role.
Specifically, \set{x} defines the set of random variables for which we are interested in their distributions.
Each \Qvar represents a random variable whose distribution is important to us, and each \rv{e} corresponds to the
evidence that is available for that variable.

For a parametric model (as defined in Definition~\ref{def:param-model}), it seems reasonable to define a conditional
form of our divergence measure, conditioned on the value of the parameter.

To do so, in Equation~\ref{eq:div_measure}, we replace normal expectation with conditional expectation.
There will be no longer a need to maximize over different distributions, since in a parametric model the parameter
fully determines the distribution of the sample space.

\begin{definition}[Conditional Divergence Measure]
    \label{def:cond_divergence}
    Assume that \pmodel is a parametric model, and $\Xpairs$ is a query set.
    We define the \emph{divergence measure of $P \in \set{P}$ given $\paramValue$ for \Qset} as follows:
    \begin{align}
        \DxCond &= \DxCondExpand \\
        &= \DxCondExpandFull \cdot
        \label{eq:cond_div_measure}
    \end{align}
\end{definition}

Even if we cannot find a distribution that has a small divergence from every distribution, still using the distribution
that minimizes the maximum divergence seems a reasonable choice.

In a parametric model, the maximum of divergence happens for a prior distribution
that is concentrated at a single value of the parameter $\paramValue$.
That means, for a parametric model which allows any high peak prior, instead of maximizing over the set of
all acceptable distributions, we can simply maximize over the parameter space, using the conditional version
of the divergence measure.



\begin{lemma}
    \label{lm:DxP_uppper_bound}
    Assume that \pmodel is a parametric model.
    Let \Xpairs be a query set in \Mt.
    For every $P \in \set{P}$ we have
    \begin{equation*}
        \Dx \leq \maxParam \DxCond
    \end{equation*}
\end{lemma}

\begin{proof}
    \newcommand{\RP}{\sumixe \pi(\xeIt[i]) \ln \frac{R(\xIe[i])}{P(\xIe[i])}}

    Let $R$ and $P$ be two arbitrary probability measures in \Mt.
    For every parameter value \paramValue we have:
    \[
        \DxCond[P] - \DxCond[R] = \RP \cdot
    \]
    Conditional divergence is always positive and we have
    \[
        \RP \leq \DxCond \cdot
    \]
    This inequality holds for any \paramValue.
    Therefore, the maximum of the right-hand side w.r.t. \paramValue is also greater than or equal to the
    maximum of the left-hand side:
    \begin{equation}
        \maxParam \RP \leq \maxParam \DxCond \cdot
        \label{eq:ineq-theorem1}
    \end{equation}
    Trivially, for every \paramValue we have
    \[
        \RP \leq \maxParam \RP \cdot
    \]
    \Mt is a parametric model and $\marginalEq[R]{\xe[i]}$, where $r(\paramValue)$ is
    a prior probability distribution.
    Since this inequality holds for every value of \paramValue and $r(\paramValue) \geq 0$, we can multiply both
    sides by $r(\paramValue)$, and integrate.
    Notice that the right hand side is not a function of $\paramValue$ and it remains unchanged
    because $\int \dt[r] = 1$:
    \[
        \DxExpand[R] \leq \maxParam \RP\cdot
    \]
    Now from Inequality~\ref{eq:ineq-theorem1}, for \emph{any} $P \in \set{P}$ and $R \in \set{P}$, it
    follows that
    \[
        \DxExpand[R] \leq \maxParam \DxCond,
    \]
    which proves the lemma.
\end{proof}


\begin{theorem}
    \label{th:Dx_parametric_form}
    Suppose \pmodel is a parametric model.
    Let \Qvar be a query variable, and \Evar be an evidence variable in \Mt.
    If for every value of $\paramValue$ there is a distribution $R \in \set{P}$ such that
    $R(\rval[]{s}) = \pi(\rval[]{s} \mid \paramValue)$ for every $\rval[]{s} \in \set{S}$,
    then for any $P \in \set{P}$ we have:
    \begin{equation}
        \Dxe = \maxParam \DxeCond\cdot
        \label{eq:div_parametric}
    \end{equation}
    \label{th:div_for_parametric}
\end{theorem}

\begin{proof}
    For an arbitrary distribution $P \in \set{P}$, we let
    \[
        \paramValue^* = \arg\maxParam \DxeCond \cdot
    \]
    In \Mt there should be a distribution $R \in \set{P}$ that equals $\pi(\rval[]{s} \mid \paramValue^*)$
    for every $\rval[]{s} \in \set{S}$.
    Obviously, $R$ and $\pi(\cdot \mid \paramValue)$ define the same distribution for any random variable,
    and we have
    \begin{equation}
        \label{eq:th1}
        \Ex{R}{\Dcond[R]} = \DxCondExpand[][\paramValue^*] \cdot
    \end{equation}
    On the other hand
    \[
        \maxQ \Ex{Q}{\Dcond} \geq \Ex{R}{\Dcond[R]}\cdot
    \]
    Notice that the left hand side is $\Dxe$, and by Equation~\ref{eq:th1}
    \[
        \Dxe \geq \maxParam \DxeCond \cdot
    \]
    This inequality and Lemma~\ref{lm:DxP_uppper_bound} prove the theorem.
\end{proof}


\begin{proposition}
    Let \Qvar be a query variable, and \Eset be an evidence set in \Mt.
    If the conditions of Theorem~\ref{th:div_for_parametric} holds, then for any $P \in \set{P}$ we have:
    \[
        \Dx = \maxParam \DxCond{P}{\Eset} \cdot
    \]
\end{proposition}


\begin{lemma}
    Let $p$, and $q$ be two probability distributions for a random variable $\Theta$.
    If for any $\theta$, and a constant $\lambda$, we have
    \[
        \ln \frac{p(\theta)}{q(\theta)} = \lambda
    \]
    then $\lambda = 0$.
\end{lemma}

\begin{proof}
    Suppose, for the sake of contradiction, that $\lambda > 0$.
    This implies for every $\theta$ we have
    \[
        \frac{p(\theta)}{q(\theta)} > 1 \cdot
    \]
    Since $q(\theta) > 0$, we can conclude that $p(\theta) > q(\theta)$.
    This inequality holds for every $\theta$, and therefore
    \[
        \int \dt[p] > \int \dt[q],
    \]
    which is a contradiction.

    If we assume $\lambda < 0$, similarly we can conclude $\int \dt[p] < \int \dt[q]$, which is a contradiction again.
    Hence, $\lambda$ cannot be positive or negative and we must have $\lambda = 0$.
\end{proof}

\begin{theorem}
    \label{th:lambda}
    Let \Qvar be a query variable, and \Evar be an evidence variable in a parametric model \pmodel.
    Assume that each value of the parameter \paramValue, can be represented as a pair $(\ab)$, and for
    every
    \paramA, \paramB, and \rval{e} we have
    \begin{equation}
        \label{eq:th-lambda-independece}
        p(\bIa, \rval{e}) = p(\bIa) \cdot
    \end{equation}

    If for some probability measure $P \in \set{P}$, the conditional divergence of $P$ is a real valued function
    of \paramA:
    \begin{equation*}
        \DxeCond = \lambda(\paramA),
    \end{equation*}
    then $P$ is the central distribution for $\QvarIE$, and
    \begin{equation*}
        \lambda(\paramA) = \ln \int \phiFunc d\paramB,
    \end{equation*}
    where
    \begin{equation*}
        \phiFunc = \phiExp \cdot
    \end{equation*}

\end{theorem}

\begin{proof}
    \newcommand{\lambdaFunc}{\lambda(\paramA)}
    By Bayes' theorem and Equation~\ref{eq:th-lambda-independece} we have
    \begin{align*}
        \frac{\pi(\xIet)}{P(\xIe)} &= \frac{p(\tIxe)}{p(\bIa, \rval{e})p(\paramA \mid \rval{e})} \\
        &= \frac{p(\tIxe)}{p(\bIa)p(\paramA \mid \rval{e})} \cdot
    \end{align*}
    Now, by simple algebra we can verify that
    \begin{equation*}
        \DxeCond = \ln \frac{\phiFunc}{p(\bIa)}
    \end{equation*}
    We let
    \begin{equation*}
        \rhoFunc = \frac{\phiFunc}{\int \phiFunc d\paramB}
    \end{equation*}
    Therefore,
    \begin{equation*}
        \DxeCond = \lambdaFunc + \ln \frac{\rhoFunc}{p(\bIa)}
    \end{equation*}
    where
    \[
        \lambdaFunc =  \ln \int \phiFunc d\paramB
    \]
\end{proof}

\begin{definition}[Generic Parametric Model]
    We say a parametric model \pmodel is \emph{generic}, if for any arbitrary probability distribution $r$,
    there is a probability measure $R \in \set{P}$, such that for every $\rval[]{s} \in \set{s}$
    \[
        \marginalEq[r]{\rval[]{s}}\cdot
    \]
\end{definition}

\begin{proposition}
    A generic parametric model satisfies the conditions of Theorem~\ref{th:Dx_parametric_form}.
\end{proposition}

\begin{theorem}[Minimax theorem~\cite{Du1995}]
    \label{th:minimax}
    Let $\set{X} \subset \mathbb {R}^{n}$ and $\set{Y} \subset \mathbb {R}^{m}$ be compact convex sets.
    If $f:\set{X}\times \set{Y}\rightarrow \mathbb {R}$ is a continuous function that is concave-convex, i.e.

    \begin{itemize}
        \item $f(\cdot ,y):\set{X}\to \mathbb {R}$ is concave for fixed $y$, and
        \item $f(x,\cdot ):\set{Y}\to \mathbb {R}$ is convex for fixed $x$.
    \end{itemize}
    Then we have that
    \begin{equation}
        \max_{x\in \set{X}}\min_{y\in \set{Y}}f(x, y) = \min_{y\in \set{Y}}\max_{x\in \set{X}}f(x,y)\cdot
        \label{eq:minimax}
    \end{equation}
\end{theorem}


\begin{theorem}
    \label{th:central_by_max}
    Consider a generic parametric model \pmodel, and let \Qvar be a query variable, and \Evar be an evidence
    variable in \Mt.
    Suppose that for every probability measures $Q_1, Q_2 \in \set{P}$, and any real number $0 \leq \alpha \leq 1$,
    there is a $Q^* \in \set{P}$, such that for every $\xe$ we have
    \begin{equation}
        Q^*(\xIe) = \convexCond{\xIe}\cdot
        \label{eq:convex_dist_set}
    \end{equation}

    In this model, the central distribution for $\QvarIE$ can be obtained by:
    \begin{align}
        \centralE &= \arg\maxP \int \DxeCond \dt\\
        &= \arg\maxP \Dminimax,
        \label{eq:Cx_by_max}
    \end{align}
    where $\marginalEq[p]{\rval[]{s}}$, for every $\rval[]{s} \in \set{s}$.
\end{theorem}

\begin{proof}
    \newcommandx{\f}[2][1 = r, 2 = P_{\XIE}]{ f(#1, #2)}
    We prove this theorem using the Minimax theorem.
    For that, we define a functional as follows:
    \begin{equation*}
        \f = \int \DxCondExpand \dt[r],
    \end{equation*}
    where $r(\paramValue)$ is an arbitrary probability distribution, and $P_{\XIE}$ represents different
    distributions of \Qvar given different values of \Evar, induced by a probability measure $P \in \set{P}$.

    Since $r(\paramValue)$ can be any distribution, maximizing with respect to $r$ is similar to maximizing
    with respect to $\paramValue$, and we have
    \[
        \centralE = \arg\minP \max_{r} \f\cdot
    \]

    The domain of $r$ is the set of all probability distributions, which is a compact convex set.
    Moreover, from Equation~\ref{eq:convex_dist_set}, it follows that the domain of $P_{\XIE}$ , which is a function
    of both \Qvar and \Evar, is also a compact convex set.
    Thus, the domain of the functional $\f$ is a compact convex set.

    For a fixed $P_{\XIE}$, $\f[\cdot]$ is a linear function, which is both concave and convex.

    On the other hand, for a fixed $r$, if we let $\marginalEq[r]{\xe}$ we have
    \begin{equation}
        \f[r][\cdot] = c - \sumxe R(\xe) \ln P(\xIe),
        \label{eq:max_for_P}
    \end{equation}
    where $c$ is not a function of $P_{\XIE}$.
    If we calculate the Hessian matrix of $\f[r][\cdot]$, with respect to $P_{\XIE}$, we observe that the matrix is
    diagonal, and each element of the main diagonal is $\frac{R(\xIe)}{P(\xIe)^2}$.
    Thus, the hessian matrix of $\f[r][\cdot]$ is positive semi-definite and $\f[r][\cdot]$ is a convex function.
    Consequently, by Theorem~\ref{th:minimax}
    \begin{equation}
        \minP \max_{r} \f = \max_{r} \minP \f\cdot
        \label{eq:divergence_minmax}
    \end{equation}
    From Equation~\ref{eq:max_for_P} we can see that for an arbitrary fixed $r$ we have
    \[
        \minP \f = \maxP \sumxe R(\xe) \ln P(\xIe)\cdot
    \]

    We know that the Kullback–Leibler divergence, and therefore its expected value, is non-negative:
    \[
        \Ex{R}{\Dcond[R]} \geq 0\cdot
    \]
    By simple algebra we get
    \[
        \sumxe R(\xe) \ln P(\xIe) \leq \sumxe R(\xe) \ln R(\xIe)\cdot
    \]
    Recall that \Mt is a generic parametric model.
    That implies $R \in \set{P}$, and we can reach this upper bound by letting $P = R$:
    \[
        \minP \f = \Dminimax[R]\cdot
    \]
    By Equation~\ref{eq:divergence_minmax}, we conclude
    \[
        \centralE = \arg\max_{R \in \set{P}} \int \DxeCond[R] \dt[r] \cdot \qedhere
    \]
\end{proof}

Theorem~\ref{th:central_by_max} requires that in our model the set of acceptable distribution for $\QvarIE$ be a convex
set.
In most cases, this condition cannot be satisfied.
However, if the distribution that is obtained by Equation~\ref{eq:Cx_by_max} is an acceptable distribution in our model,
the theorem still implies that it is a central distribution in our model.
Note that the set of probability distributions is convex.

\begin{theorem}
    \label{th:lambda}
    Under the assumptions of Theorem~\ref{th:central_by_max}, the central distribution for $\QvarIE$ satisfies:
    \begin{equation}
        \DxeCond[\centralE] = \lambda,
        \label{eq:lambda}
    \end{equation}
    where $\lambda$ is a constant.
\end{theorem}
\begin{proof}
    By Theorem~\ref{th:central_by_max}, the central distribution for $\QvarIE$ maximizes
    \[
        \functional{p(\paramValue)} = \Dminimax,
    \]
    with respect to different choices of the prior distribution $p(\paramValue)$, subject to the
    constraint $\int \dt[p] = 1$.

    Applying the Lagrange multiplier technique, the local maximum of $\functional{}$ is a stationary point of the
    Lagrangian functional:
    \[
        \Lagr[p(\paramValue)] = \Dminimax - \lambda \left( \int \dt - 1 \right)\cdot
    \]
    Let us denote the prior distribution corresponding to the central distribution \centralE by $\cPrior$.
    Let $p(\paramValue) = \cPrior + \epsilon \eta(\paramValue)$ be a variation of $\cPrior$, where $\eta(\paramValue)$ is
    a continuously differentiable function with $\eta(0) = \eta(1) = 0$, and $\epsilon$ is a small constant.

    Since $\cPrior$ is an extremizing function for $\functional{p(\paramValue)}$, the lagrangian
    $\Lagr$ has a stationary point where $\epsilon = 0$, and we have
    \[
        \parDerivAt[\Lagr] = 0\cdot
    \]
    Note that
    \begin{align*}
        \de{p(\paramValue)} &= \eta(\paramValue),\\
        \de{P(\xe)} &= \marginal[\eta]{\xe},\\
        \de{P(\rval{e})} &= \marginal[\eta]{\rval{e}}\cdot
    \end{align*}
    Using the chain rule of calculus, we calculate the partial derivative of $\Lagr$ relative to $\epsilon$:
    \begin{align*}
        \parDeriv\ =\ &\int \left( \Dparam  \right) \dt[\eta] \\
        &- \int \left( \sumxe \pi(\xeIt) \frac{\marginal[\eta]{\xe}}{P(\xe)} \right) \dt \\
        &+ \int \left( \sum_{\rval{e}} \pi(\eIt) \frac{\marginal[\eta]{\rval{e}}}{P(\rval{e})} \right) \dt \\
        &- \int \lambda \dt[\eta]
    \end{align*}
    Since $\marginalEq{\xe}$ and $\marginalEq{\rval{e}}$, we get
    \begin{equation*}
        \parDeriv = \int \left(-\lambda + \Dparam \right) \dt[\eta]\cdot
    \end{equation*}
    We let $ \parDerivAt = 0$.
    Since $\eta(\paramValue)$ is an arbitrary function, by applying the fundamental lemma of the calculus of
    variations and letting $\epsilon = 0$, for every value of $\paramValue$ we have
    \[
        \Dparam[\centralE] = \lambda\cdot \qedhere
    \]
\end{proof}

Consider a scenario where we are trying to predict the outcome of a four-sided dice. This dice is unfair, with each
face marked by a binary number: $00$, $01$, $10$, and $11$.
Before making our prediction, we can roll the dice for several times and use the results to learn the associated
probabilities.
We assume that the dice rolls are independent.

Let's focus on determining the central distribution for this problem.
The first step in this process is to establish our query set $\Xpairs$.

In a prediction problem, we are interested in the distribution of the random variable we want to predict,
conditioned on the observed data.
For example, if we roll the dice for three times before making our prediction,
we will need $P(\rv[4]{x} \mid \rv[1]{x},\rv[2]{x},\rv[3]{x})$, where \Qvar denotes the outcome
of the $i$-th dice roll.

Thus, one natural way for defining a query set $\Xpairs$ is to let each \Qvar be the outcome of
the $i$-th dice roll, and define each \rv{e} as a vector of the previous dice outcomes $(\seqRv{i-1})$.

Now let us calculate the conditional divergence measure for \set{x} as defined in Definition~\ref{def:cond_divergence}:
\newcommand{\seqvalxx}[1][x]{\rval[1]{#1}, \rval[2]{#1}}
\begin{align*}
    \DxeCond &= \KLcond{\rval[1]{x}}{} \\
    &+ \KLcond{\rval[2]{x}}{\rval[1]{x}} \\
    &+ \KLcond{\rval[3]{x}}{\seqvalxx} \\
    &+ \ \cdots \\
    &+ \KLcond{\rval[n]{x}}{\seqRval{n-1}}\cdot
\end{align*}
After factoring out $\pi(\seqRval{n} \mid \paramValue)$ from every term, we use the chain rule for conditional
probability:
\begin{align*}
    \DxeCond &=
    \sum_{\seqRval{n}} \pi(\seqRval{n} \mid \paramValue) \ln
    \frac
    {\pi(\rval[1]{x} \mid \paramValue) \pi(\rval[2]{x} \mid \rval[1]{x}, \paramValue)
    \cdots \pi(\rval[n]{x} \mid \seqRval{n-1}, \paramValue)}
    {P(\rval[1]{x}) P(\rval[2]{x} \mid \rval[1]{x}) \cdots P(\rval[n]{x} \mid \seqRval{n-1})} \\
    &= \KLcond{\seqRval{n}}{} \cdot
\end{align*}
By Equation~\ref{eq:Cx_by_max}, for the central distribution we have
\begin{align*}
    \central &= \arg\max_{P} \int \left(\KLcond{\seqRval{n}}{}\right) \dt \\
    &= \arg\max_{P} \int \sum_{\seqRval{n}} p(\seqRval{n}, \paramValue) \ln
    \frac{p(\paramValue \mid \seqRval{n})}{p(\paramValue)} d\paramValue \cdot
\end{align*}

That implies, the central distribution for our problem is the same as the distribution we obtain when using the
reference prior~\cite{BERNARDO200517} for our main parameter.

Imagine playing a game of chance involving our four-sided dice.
After rolling the dice, we input the outcome into a mysterious machine.
The machine then announces whether we have won or lost the game.
We have no clue how the machine works. We are not even sure if the dice outcome truly affects the machine’s output.
All we know is that the machine is memory-less, and the result of each game is independent.

Our goal is to learn how the machine operates through experimentation.
We aim to be able to predict whether we will win the game after observing the dice outcome.

We assume that, first, we roll the dice $n$ times, and record each outcome.
Next, we input some of these dice outcomes into the machine and observe the result of each game.
As we will see, this assumption is important for deriving the central distribution more easily.

Let us define a query set for this problem.
We denote this set as $\Xpairs$, where each \Qvar is the result of the $i$-th game, and the evidence \rv{e} is a
vector
\[
    (\seqRv{i-1}, \seqRv[y]{n}),
\]
where each \rv{y} denotes the $i$-th dice outcome.

The conditional divergence for \set{x} can be obtained by
\begin{align*}
    \DxeCond &= \KLcond{\rval[1]{x}}{\seqRval[y]{n}} \\
    &+ \KLcond{\rval[2]{x}}{\rval[1]{x},\seqRval[y]{n}} \\
    &+ \KLcond{\rval[3]{x}}{\seqvalxx, \seqRval[y]{n}} \\
    &+ \ \cdots \\
\end{align*}
After using the chain rule for conditional probability the right hand side simplifies to
\begin{align*}
    \KLcond{\seqRval{n}}{\seqRval[y]{n}} \cdot
\end{align*}

Consequently, an alternative way for defining our query set is to define it as a single
pair $\left\{(\rvec{x}, \rvec{e})\right\}$, where \rvec{x} is the vector of $n$ game's result, and \rvec{e} is the vector of $n$
dice outcome.

Using the new definition for \set{x}, by Equation~\ref{eq:lambda} we have:
\begin{equation*}
    \KLcond[\central]{\vval{x}}{\vval{e}} = \lambda
\end{equation*}
\emph{derive a $\paramValue = (\paramA, \paramB)$ closed form for central dist...}

\[
    \frac{\pi(\vval{x} \mid \vval{e}, \paramValue)}{\central(\vval{x} \mid \vval{e})}
    = \frac{\pi(\paramValue \mid \vval{x}, \vval{e})}{\central(\paramValue \mid \vval{e})}
\]

sdfd

\[
    \KLabVec
\]

Assume that we decide to simplify our learning task.
We choose to consider only the least significant digit of the dice outcome and ignore the other digit.
For example, if the dice outcome is $10$, we treat it as $0$.
This approach decreases the number of possible outcomes of the dice, making the learning process simpler.
However, it also reduces our ability to predict the game’s result accurately.

In order to find a central distribution for this version of our game, we should slightly modify the definition of the
query set.
While each \Qvar remains unchanged, we need to represent each \rv{e} as a vector
\[
    (\seqRv{i-1}, \seqRv[y']{n}),
\]
where each \rv{y'} represents the least significant digit of the dice outcome.
We denote this new query set as \set{x'} and the previous query set as \set{x}.

Following similar steps as we did for \set{x}, we can show that \set{x'} also has a more compact counterpart,
which includes a single pair $(\rvec{x}, \rvec{e'})$, where \rvec{x} is the vector $(\seqRv{n})$, and \rvec{e'} is
the vector
$(\seqRv[y']{n})$.

\emph{explain how the central distribution for this version is different...}

When we have a lot of learning data, there is no point in using this simpler version of our learning task.
However, when the available data is not enough for the more complex version, the simpler version can still produce
relatively meaningful results,
while the data is too small for the more complex version.

Is it possible to have a probabilistic inference framework that is able to automatically choose between these two
versions of the problem based on the quality and amount of available data?
It seems that the central distributing has this ability.
For that, we need to use the central distribution for the query set $\set{x} \cup \set{x'}$.
This seems reasonable, since when we want our probabilistic inference framework to choose between two versions of
our problem, our query set should include random variables of both versions.

\begin{theorem}
    Let \pmodel be a generic parametric model, and $\Xsingles$ be a set of random variables in \Mt.
    Let $\paramFunc$, for every $i$, be a function of the parameter $\param$ that fully parametrizes \Qvar,
    so that for $\paramFuncValue = \paramFunc(\paramValue)$ we have:
    \begin{equation}
        \pi(\xIt) = \pi \left( \rval{x} \mid \paramFuncValue \right)\cdot
        \label{eq:func_of_theta}
    \end{equation}
    The prior distribution corresponding to the central distribution for \set{X} in \Mt can be characterized
    by the following fixed point equation:
    \begin{equation}
        \cPrior \propto \left( \prod_i \cMass{\tIw} \rhoPrior \right)^{\frac{1}{|\set{x}|}},
        \label{eq:fixed_point_cx}
    \end{equation}
    where
    \[
        \rhoPrior \propto \exp \left\{\sum_{\rval{x}} \pi(\xIw) \ln \cMass{\wIx} \right\}\cdot
    \]

\end{theorem}

\begin{proof}
    First, we show that the set of distributions of each \Qvar is a convex set.
    Let $Q^*(\rval{x}) = \convexCond{\rval{x}}$, for some $Q_1, Q_2 \in \set{P}$, $0 \leq \alpha \leq 1$ and
    arbitrary $i, \rval{x}$.

    \Mt is a parametric model.
    Therefore,
    \begin{align*}
        Q^*(\rval{x}) &= \alpha \marginal[q_1]{\rval{x}} + (1 - \alpha) \marginal[q_2]{\rval{x}}\\
        &= \int \pi(\xIt) (\convexCond[q]{\paramValue}) d\paramValue\cdot
    \end{align*}
    $\convexCond[q]{\paramValue}$ is a valid prior distribution and \Mt is a generic parametric model.
    That implies $Q^* \in \set{P}$.

    Thus, by Theorem~\ref{th:lambda} the central distribution of \set{X} satisfies
    \begin{equation}
        \sumOverix \pi(\xIt) \ln \frac{\pi(\xIt)}{\central(\rval{x})} = \lambda\cdot
        \label{eq:lambda_th_proof}
    \end{equation}
    Moreover, from Equation~\ref{eq:func_of_theta} and Bayes' theorem it follows
    \begin{align*}
        \sumOverix \pi(\xIt) \ln \frac{\pi(\xIt)}{\central(\rval{x})}
        &= \sumOverix \pi(\xIw) \ln \frac{\pi(\xIw)}{\central(\rval{x})}\\
        &= \sumOverix \pi(\xIw) \ln \frac{\cMass{\wIx}}{\cPrior[(\paramFuncValue)]}\\
        &= \sum_i \ln \frac{\rhoPrior}{\cPrior[(\paramFuncValue])}\cdot
    \end{align*}
    Since each $\paramFunc$ is a function of $\param$, for $\paramFunc(\paramValue) = \paramFuncValue$
    we have $\cMass{\paramValue, \paramFuncValue}=\cPrior$.
    Therefore,
    \begin{equation*}
        \cPrior[(\paramFuncValue)] = \frac{\cPrior}{\cMass{\tIw}}\cdot
    \end{equation*}
    Now we rewrite Equation~\ref{eq:lambda_th_proof}:
    \begin{align*}
        |\set{X}| \ln \cPrior &= \sum_i \ln \left(\cMass{\tIw} \rhoPrior \right) - \lambda\\
        \cPrior &= \left( e^{-\lambda} \prod_i \cMass{\tIw} \rhoPrior \right)^{\frac{1}{|\set{x}|}} \qedhere
    \end{align*}
\end{proof}


\begin{theorem}
    Let \pmodel be a generic parametric model, and $\Xpairs$ be a set of random variables in \Mt.
    Let $\paramFunc$, for every $i$, be a function of the parameter $\param$ that fully parametrizes \Qvar,
    so that for $\paramFuncValue = \paramFunc(\paramValue)$ we have:
    \begin{equation}
        \pi(\xIt) = \pi \left( \rval{x} \mid \paramFuncValue \right)\cdot
        \label{eq:func_of_theta}
    \end{equation}
    The prior distribution corresponding to the central distribution for \set{X} in \Mt can be characterized
    by the following fixed point equation:
    \begin{equation}
        \bIaRoot \propto \left( \prod_i \frac{\abIab \rhoPrior}{\aIa} \right)^{\frac{1}{|\set{x}|}},
        \label{eq:fixed_point_cx}
    \end{equation}
    where
    \[
        \rhoPrior \propto \exp \left\{ \sumxe \xeIba \ln \bIxe \right\} \cdot
    \]

\end{theorem}

\begin{proof}
    First, we show that the set of distributions of each \Qvar is a convex set.
    Let $Q^*(\xIe) = \convexCond{\xIe}$, for some $Q_1, Q_2 \in \set{P}$, $0 \leq \alpha \leq 1$ and
    arbitrary $i, \xe$.

    \Mt is a parametric model.
    Therefore,
    \begin{align*}
        Q^*(\xIe) &= \alpha \int \xIebFull q_1(\beta \mid \rval {e}) d\beta + (1 - \alpha) \marginal[q_2]{\rval{x}}\\
        &= \int \pi(\xIt) (\convexCond[q]{\paramValue}) d\paramValue\cdot
    \end{align*}
    $\convexCond[q]{\paramValue}$ is a valid prior distribution and \Mt is a generic parametric model.
    That implies $Q^* \in \set{P}$.

    Thus, by Theorem~\ref{th:lambda} the central distribution of \set{X} satisfies
    \begin{equation}
        \Dparam[\central] = \lambda\cdot
        \label{eq:lambda_th_proof}
    \end{equation}
    Moreover, from Equation~\ref{eq:func_of_theta} and Bayes' theorem it follows
    \begin{align*}
        \lambda
        &= \Dparam[\central]\\
        &= \sumxe \xeIba \ln \frac{\xIeb}{\central(\xIe)} \\
        &= \sumxe \xeIba \ln \frac{\bIxe}{\cMass(\paramB \mid \rval{e})} \\
        &= \sum_i \ln \frac{\rhoPrior}{\bIa}\cdot
    \end{align*}
    Since each $\paramFunc$ is a function of $\param$, for $\paramFunc(\paramValue) = \paramFuncValue$
    we have $\cMass{\paramValue, \paramA, \paramB}=\cPrior$ $\cMass{\alpha , \paramA} = \cMass{\alpha}$.
    Therefore,
    \begin{equation*}
        \bIa = \frac{\aIa}{\abIab} \bIaRoot \cdot
    \end{equation*}
    Now we rewrite Equation~\ref{eq:lambda_th_proof}:
    \[
        |\set{X}| \ln \bIaRoot = -\lambda + \sum_i \ln \frac{\abIab \rhoPrior}{\aIa}
    \]
    Then:
    \begin{align*}
        \bIaRoot
        &= \left( e^{-\lambda} \prod_i \frac{\abIab \rhoPrior}{\aIa} \right)^{\frac{1}{|\set{x}|}} \\
        &= \left( e^{-\lambda} \prod_i \frac{\bIaRoot \rhoPrior}{\bIa} \right)^{\frac{1}{|\set{x}|}} \\
        &= \bIaRoot \left( \prod_i \frac{ \rhoPrior}{\bIa} \right)^{\frac{1}{|\set{x}|}} \\
        &= \bIaRoot \left(e^{-\lambda} \prod_i
        \frac{\rhoPrior[(\paramA, \paramB) \cMass(\paramA)]}{\cMass(\paramA, \paramB) \rhoPrior[(\paramA)] } \right)
        ^{\frac{1
        }{|\set{x}|}}
        \qedhere
    \end{align*}
\end{proof}






Let’s revisit our discussion from the previous section.
We saw that in Bayesian framework when we have evidence \rv{e'}, such that $\rv{e'} = f(\rv{e})$, the
optimal strategy for \rv{e} always has a greater expected utility than any strategy that uses \rv{e'}.
We stated that we believe...


\begin{definition}[Aggregator]
    Consider two probabilistic models \model and \aggmodel.
    Let \Qvar be a query variable and $\Eset = \{\seqRvInf[e]\}$ be an evidence set in \M.
    Also, let \agg{\rv{e}}, \agg{\Qvar}, and \rv{i} be random variables defined on \agg{\set{s}} in \Magg.
    We refer to \agg{\rv{x}}, \agg{\rv{e}} as the \emph{aggregated} query and evidence variables, and \rv{i} as the
    \emph{selector} variable.

    Suppose that for a probability measure $P \in \set{P}$ there exists a probability measure
    $\agg{P} \in \agg{\set{P}}$, such that for any index \rval{i}, and every values \QvarVal, and \rval[i]{e}
    there is some \agg{\QvarVal}, and \agg{\rval{e}}, where we have
    \begin{equation}
        P(\Qvar = \QvarVal, \rv[i]{e} = \rval[i]{e}) =
        \agg{P}(\agg{\Qvar} = \agg{\QvarVal}, \assign{\agg{e}} \mid \assign{I}) \cdot
        \label{eq:th1-1}
    \end{equation}
    Furthermore, \agg{\Qvar} and \rv{I} are conditionally independent given \agg{\rv{E}}:
    \begin{equation}
        \agg{P}(\aggXIE, \rv{I}) = \agg{P}(\aggXIE) \cdot
        \label{eq:th1-2}
    \end{equation}
    We call \agg{P} an \emph{aggregator of $P$ with respect to $\QvarIEset$}.
\end{definition}

\begin{proposition}
    By Equations~\ref{eq:th1-1} and~\ref{eq:th1-2} we have
    \begin{equation*}
        P(\QvarVal \mid \rval[i]{e}) = \agg{P}(\aggxIe) \cdot
    \end{equation*}
\end{proposition}

\begin{definition}[Aggregate Model]
    \label{def:aggregate-model}
    Consider a probabilistic model \model.
    Let \Qvar be a query variable, and \Eset be an evidence set in \M.
    We say a model \aggmodel is the \emph{aggregate model} of \M with respect to $\QvarIEset$,
    If every probability measure in \Magg is the aggregator of a probability measure in \M with respect to $\QvarIEset$.
    %, and every probability measure in \M has at least one aggregator in \Magg with respect to $\QvarIEset$.
\end{definition}

\begin{definition}[Selective Aggregate Model]
    Let \Qvar be a query variable, and \Eset be an evidence set in \model.
    Let \Magg be an aggregate model of \M with respect to $\QvarIEset$.
    We say \Magg is \emph{selective}, if for every $P \in \set{P}$ and any value \rval{i} of the selector
    variable \rv{I}, there is an aggregator of $P$ in \Magg, such that $\agg{P}(i) = 1$.

\end{definition}


\begin{theorem}
    Let \Qvar be a query variable, and \Eset be an evidence set in a probabilistic model \model.
    Suppose that \aggmodel is a selective aggregate model of \M with respect to $\QvarIEset$.
    Let \agg{\rv{x}}, \agg{\rv{e}} be the aggregated query and evidence variables in \Magg.
    If $\agg{P} \in \agg{\set{P}}$ is an aggregator of the probability measure $P \in \set{P}$
    with respect to $\QvarIEset$, then we have
    \begin{equation*}
        \Dx = \aggDxP \cdot
    \end{equation*}

    In addition, the central distribution for $\agg{\Qvar}|\agg{\rv{e}}$ is an aggregator of the central
    distribution for $\QvarIEset$.
\end{theorem}

\begin{proof}
    \newcommand{\aggExpKL}[1]{\ExpKL[\agg{\rval{x}}][\agg{\rval{e}}][\agg{#1}][\agg{P}]}
    Suppose $\agg{P} \in \agg{\set{P}}$ is an aggregator of the probability measure $P \in \set{P}$
    with respect to $\QvarIEset$.
    Let
    \begin{equation*}
        \agg{R} = \arg\max_{\agg{Q} \in \agg{\set{P}}} \aggExpKL{Q}.
    \end{equation*}
    Since \Magg is an aggregate model, $\agg{R}$ must be an aggregator of some probability measure $R \in \set{P}$.
    It follows that
    \begin{align*}
        \aggDxP
        &= \aggExpKL{R} \\
        &= \sum_i \agg{R}(\rval{i}) \ExpKL[][{\rval[i]{e}}][R] \\
        &\leq \max_i \ExpKL[][{\rval[i]{e}}][R] \cdot
    \end{align*}
    This implies
    \begin{equation}
        \aggDxP \leq \Dx \cdot
        \label{eq:th-2-proof-1}
    \end{equation}

    Similarly, let
    \begin{equation*}
    (S,k)
        = \arg\max_{(Q,i)} \ExpKL[][{\rval[i]{e}}] \cdot
    \end{equation*}
    \Magg is a selective aggregate model.
    This means that $S$ must have an aggregator \agg{S} in \Magg, which selects $k$ by assigning it a
    probability of 1: $\agg{S}(k) = 1$.
    Therefore,
    \begin{align*}
        \Dx
        &= \ExpKL[][{\rval[k]{e}}][S] \\
        &= \sum_{\aggxe} \agg{S}(\aggxe \mid k) \ln\frac{\agg{S}(\aggxIe)}{\agg{P}(\aggxIe)} \\
        &= \aggExpKL{S} \\
        &\leq \aggDxP \cdot
    \end{align*}
    From this and Inequality~\ref{eq:th-2-proof-1}, we conclude that
    \begin{equation*}
        \Dx = \aggDxP \cdot
    \end{equation*}

    To prove the second part of the theorem, let \agg{C} be a central distribution
    for $\agg{\Qvar}|\agg{\rv{e}}$.
    Since \Magg is an aggregate model for \M, \agg{C} must be an aggregator for some probability
    measure $C \in \agg{\set{P}}$.
    If we assume, by contradiction, that $C$ is not a central distribution for $\QvarIEset$ in \M, then there must
    be a probability
    measure $R \in \set{P}$ such that:
    \begin{equation*}
        \Dx[R] < \Dx[C] = \aggDxP[C] \cdot
    \end{equation*}
    On the other hand, since \Magg is a selective model, $R$ must have an aggregator $\agg{R} \in \agg{\set{P}}$,
    and since \agg{C} is a central distribution in \Magg, we have
    \begin{equation*}
        \Dx[R] = \aggDxP[R] \geq \aggDxP[C],
    \end{equation*}
    which is a contradiction.
\end{proof}




\bibliography{main}
\bibliographystyle{plain}